---
title: "MT Job Scrape"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("k12_he_classification.R")
```
# Scrapes Montana's K-12 and higher-ed job postings, salary, and staffing data and combines them into the datasets
# Mt_Ed_Jobs/app.R reads. Mirrors the Wyoming Education Jobs Dashboard's Wy_ED_Jobs.Rmd.

## Part 1: Montana K-12 Data

### K-12 districts scraped directly (AppliTrack, SchoolSpring, Tyler Portico, TedK12)
```{r k12 direct-platform districts, message=FALSE, warning=FALSE, echo=TRUE}
library(dplyr)
library(readr)
source("scrape_helpers.R")
source("direct_api_scrapers.R")

registry <- read.csv("k12_district_registry.csv", stringsAsFactors = FALSE)

# AppliTrack -- output columns (title/position/position2/date_posted/
# location/closing_date) already match combinedclean's shape closely; only
# District needs adding.
applitrack_districts <- registry[registry$Platform == "AppliTrack", ]
applitrack_results <- lapply(seq_len(nrow(applitrack_districts)), function(i) {
  row <- applitrack_districts[i, ]
  df <- safe_scrape(
    row$District,
    scrape_fn = function() fetch_applitrack_postings(row$Slug),
    expected_cols = c("title", "position", "position2", "date_posted", "location", "closing_date")
  )
  if (nrow(df) > 0) df$District <- row$District
  df
})
# url comes from a join back to the registry (one job-board URL per
# district, matching every other source's convention -- not a per-posting
# deep link) since AppliTrack's own fetch doesn't carry the district's URL
# through per-row.
applitrack_df <- bind_rows(applitrack_results) %>%
  left_join(select(applitrack_districts, District, Job_Link), by = "District") %>%
  transmute(title, date_posted, position = NA_character_, location, url = Job_Link, District)

# SchoolSpring / Tyler Portico -- same output shape (Title/Location/
# Posted_Date/Link), position is always recomputed from title downstream so
# it's set NA_character_ here rather than kept from the source (matching
# Wyoming's springer/SchoolSpring chunk's own convention).
schoolspring_districts <- registry[registry$Platform == "SchoolSpring", ]
schoolspring_results <- lapply(seq_len(nrow(schoolspring_districts)), function(i) {
  row <- schoolspring_districts[i, ]
  df <- safe_scrape(
    row$District,
    scrape_fn = function() fetch_schoolspring_postings(row$Slug),
    expected_cols = c("Title", "Location", "Posted_Date", "Link")
  )
  if (nrow(df) > 0) df$District <- row$District
  df
})
schoolspring_df <- bind_rows(schoolspring_results)
if (nrow(schoolspring_df) > 0) {
  schoolspring_df <- schoolspring_df %>%
    transmute(title = Title, date_posted = Posted_Date, position = NA_character_,
              location = Location, url = Link, District)
} else {
  schoolspring_df <- data.frame(title = character(0), date_posted = character(0), position = character(0),
                                 location = character(0), url = character(0), District = character(0))
}

tylerportico_districts <- registry[registry$Platform == "TylerPortico", ]
tylerportico_results <- lapply(seq_len(nrow(tylerportico_districts)), function(i) {
  row <- tylerportico_districts[i, ]
  df <- safe_scrape(
    row$District,
    scrape_fn = function() fetch_tylerportico_postings(row$Slug, row$District),
    expected_cols = c("Title", "Location", "Posted_Date", "Link")
  )
  if (nrow(df) > 0) df$District <- row$District
  df
})
tylerportico_df <- bind_rows(tylerportico_results)
if (nrow(tylerportico_df) > 0) {
  tylerportico_df <- tylerportico_df %>%
    transmute(title = Title, date_posted = Posted_Date, position = NA_character_,
              location = Location, url = Link, District)
} else {
  tylerportico_df <- data.frame(title = character(0), date_posted = character(0), position = character(0),
                                 location = character(0), url = character(0), District = character(0))
}

# TedK12 -- output columns (title/date_posted/position/location/url) already
# match combinedclean's shape; only District needs adding.
tedk12_districts <- registry[registry$Platform == "TedK12", ]
tedk12_results <- lapply(seq_len(nrow(tedk12_districts)), function(i) {
  row <- tedk12_districts[i, ]
  df <- safe_scrape(
    row$District,
    scrape_fn = function() fetch_tedk12_postings(row$Slug),
    expected_cols = c("title", "date_posted", "position", "location", "url")
  )
  if (nrow(df) > 0) df$District <- row$District
  df
})
tedk12_df <- bind_rows(tedk12_results)
if (nrow(tedk12_df) == 0) {
  tedk12_df <- data.frame(title = character(0), date_posted = character(0), position = character(0),
                           location = character(0), url = character(0), District = character(0))
}
```

### OPI "Jobs for Teachers" statewide fallback feed
```{r k12 opi statewide feed, message=FALSE, warning=FALSE, echo=TRUE}
library(dplyr)
source("scrape_helpers.R")
source("direct_api_scrapers.R")

# Montana's analog of Wyoming's WSBA vacancies page, but run differently:
# WSBA in Wyoming only ever covers the small "misc" district list that has
# no major platform. OPI's feed is genuinely statewide -- it includes the
# SAME districts already scraped directly above (Kalispell, Billings, etc.),
# so including every OPI row unfiltered would massively double-count those
# districts' postings. Filtered here to just the districts NOT already
# covered by a direct scraper (matched by whether OPI's own City field
# contains a covered district's City, from k12_district_registry.csv --
# case-insensitive, since OPI's City formatting is inconsistent, e.g. "Wolf
# Point " vs "Wolf Point, Montana").
opi_raw <- safe_scrape(
  "OPI Jobs for Teachers (statewide)",
  scrape_fn = fetch_opi_statewide_postings,
  expected_cols = c("Title", "Location", "Posted_Date", "Link")
)

covered_cities <- registry$City
is_covered <- function(location) {
  if (is.na(location)) return(FALSE)
  any(sapply(covered_cities, function(city) grepl(city, location, ignore.case = TRUE)))
}

opi_df <- opi_raw
if (nrow(opi_df) > 0) {
  opi_df <- opi_df[!sapply(opi_df$Location, is_covered), , drop = FALSE]
}

if (nrow(opi_df) > 0) {
  # District is NOT a canonical legal district name here -- OPI's feed only
  # exposes a City column, so District is that raw City value passed
  # through, the closest available proxy (same honesty tradeoff as every
  # other source's raw `location` field, just one level up). Flagged in
  # DATA_COOKBOOK.md once that's written.
  opi_df <- opi_df %>%
    transmute(title = Title, date_posted = Posted_Date, position = NA_character_,
              location = Location, url = Link, District = Location)
} else {
  opi_df <- data.frame(title = character(0), date_posted = character(0), position = character(0),
                        location = character(0), url = character(0), District = character(0))
}
```

### Combine all K-12 data, classify, archive, and accumulate history
```{r combine k12 data, echo=TRUE, warning=FALSE, message=FALSE}
library(stringr)
library(dplyr)
library(lubridate)

standardize_date <- function(x) {
  x <- as.character(x)
  x <- str_remove(x, "\\s*\\(.*\\)$")
  parsed <- parse_date_time(
    x,
    orders = c("b d Y h:M p", "B d Y h:M p", "ymd", "mdy", "dmy", "Y-m-d H:M:S"),
    tz = "UTC", quiet = TRUE
  )
  as.Date(parsed)
}

applitrack_df <- applitrack_df %>% mutate(date_posted = standardize_date(date_posted))
schoolspring_df <- schoolspring_df %>% mutate(date_posted = standardize_date(date_posted))
tylerportico_df <- tylerportico_df %>% mutate(date_posted = standardize_date(date_posted))
tedk12_df <- tedk12_df %>% mutate(date_posted = standardize_date(date_posted))
opi_df <- opi_df %>% mutate(date_posted = standardize_date(date_posted))

combined <- bind_rows(applitrack_df, schoolspring_df, tylerportico_df, tedk12_df, opi_df) %>%
  mutate(Archive_Date = Sys.Date())

# fix_title_encoding() applied once here, at the point titles first enter
# the pipeline -- see k12_he_classification.R's own header for why.
combined <- combined %>% mutate(title = fix_title_encoding(title))

if (!dir.exists("Archivek12_Data")) dir.create("Archivek12_Data")
file_name <- paste0("combined_", Sys.Date(), ".csv")
write.csv(combined, file = file.path("Archivek12_Data", file_name), row.names = FALSE)

combinedclean <- combined %>%
  mutate(position = classify_k12_position(title),
         District = canonicalize_k12_district(District)) %>%
  select(title, Archive_Date, date_posted, position, location, url, District)

if (!dir.exists("Mt_Ed_Jobs")) dir.create("Mt_Ed_Jobs")
write.csv(combinedclean, file = file.path("Mt_Ed_Jobs", "combinedclean.csv"), row.names = FALSE)

source("history_accumulator.R")

this_week_k12jobs <- combinedclean %>%
  filter(position == "Teacher") %>%
  mutate(Category = classify_k12_subject(title),
         Broad_Category = classify_k12_broad_category(Category)) %>%
  select(title, Archive_Date, position, location, url, District, Category, Broad_Category)

k12jobs <- append_weekly_rows(file.path("Mt_Ed_Jobs", "k12jobanalysis.csv"), this_week_k12jobs)
write.csv(k12jobs, file = file.path("Mt_Ed_Jobs", "k12jobanalysis.csv"), row.names = FALSE)

this_week_district_totals <- combinedclean %>%
  count(District, Archive_Date, name = "n")
k12_district_weekly_totals <- append_weekly_rows(
  file.path("Mt_Ed_Jobs", "k12_district_weekly_totals.csv"), this_week_district_totals)
write.csv(k12_district_weekly_totals, file.path("Mt_Ed_Jobs", "k12_district_weekly_totals.csv"), row.names = FALSE)

# Dedup key is title+location, not title alone -- two different schools can
# legitimately post the same generic title. See Wyoming's equivalent chunk
# for the full reasoning (unchanged here).
this_week_k12sumdistrict <- this_week_k12jobs %>%
  group_by(Broad_Category, Archive_Date, District) %>%
  summarize(sum = n_distinct(paste(title, location)), .groups = "drop")

this_week_k12sum <- this_week_k12sumdistrict %>%
  group_by(Broad_Category, Archive_Date) %>%
  summarize(sum = sum(sum), .groups = "drop") %>%
  mutate(District = "Total") %>%
  select(Broad_Category, Archive_Date, District, sum)

check_total_matches_parts(this_week_k12sum, this_week_k12sumdistrict,
                           group_cols = c("Broad_Category", "Archive_Date"))

this_week_allsum <- bind_rows(this_week_k12sum, this_week_k12sumdistrict)
Allsum <- append_weekly_rows(file.path("Mt_Ed_Jobs", "allsum.csv"), this_week_allsum)
write.csv(Allsum, file = file.path("Mt_Ed_Jobs", "allsum.csv"), row.names = FALSE)

k12districtnowsum <- this_week_k12sumdistrict %>%
  ungroup() %>%
  rename(Sum = sum) %>%
  select(Broad_Category, Sum, District)

k12nowsum <- k12districtnowsum %>%
  group_by(Broad_Category) %>%
  summarize(Sum = sum(Sum), .groups = "drop") %>%
  mutate(District = "Total")

Allnow <- bind_rows(k12nowsum, k12districtnowsum)
write.csv(Allnow, file = file.path("Mt_Ed_Jobs", "allnow.csv"), row.names = FALSE)
```

### K-12 teacher salary (MT DLI Teacher Compensation Report) and staffing (CCD teacher FTE via Urban Institute)
```{r k12 salary and staffing data, message=FALSE, warning=FALSE, echo=TRUE}
library(dplyr)
source("scrape_helpers.R")
source("salary_scrapers.R")
source("ccd_staff_scraper.R")

teacher_salary <- safe_scrape(
  "MT DLI teacher compensation",
  scrape_fn = fetch_dli_teacher_compensation_all_districts,
  expected_cols = c("District", "Teacher_Count", "Teacher_Salary_10th_Pctile",
                     "Teacher_Avg_Salary", "Teacher_Salary_90th_Pctile", "Salary_Year")
)

teacher_fte <- safe_scrape(
  "CCD district teacher FTE (MT)",
  scrape_fn = fetch_ccd_teacher_fte,
  expected_cols = c("District", "Teachers_Total_FTE", "Enrollment", "CCD_Year")
)

# Static geo/link fields (County, Latitude, Longitude, Job_Link) come from
# the district registry -- salarymap2.csv doesn't exist as its own separate
# hand-maintained file the way Wyoming's does (this project's registry
# already carries the same hand-maintained columns). A failed fetch leaves
# last run's good salary/staffing values untouched rather than blanking
# them out, same "leave it alone, don't blank it out" behavior every other
# salary/staffing chunk in this pipeline has (see Wyoming's equivalent
# chunks) -- so salarymap2.csv is read back first (if it exists) rather
# than rebuilt fresh from the registry every run.
registry <- read.csv("k12_district_registry.csv", stringsAsFactors = FALSE) %>%
  select(District, County, Latitude, Longitude, Job_Link)

salarymap2_path <- file.path("Mt_Ed_Jobs", "salarymap2.csv")
salarymap2 <- if (file.exists(salarymap2_path)) {
  read.csv(salarymap2_path, fileEncoding = "UTF-8") %>%
    select(-any_of(c("County", "Latitude", "Longitude", "Job_Link"))) %>%
    right_join(registry, by = "District") %>%
    select(District, County, Latitude, Longitude, Job_Link, everything())
} else {
  registry
}

if (nrow(teacher_salary) > 0) {
  salarymap2 <- salarymap2 %>%
    select(-any_of(c("Teacher_Count", "Teacher_Salary_10th_Pctile", "Teacher_Avg_Salary",
                      "Teacher_Salary_90th_Pctile", "Salary_Year", "Salary_Source"))) %>%
    left_join(teacher_salary, by = "District") %>%
    mutate(Salary_Source = "MT Dept. of Labor & Industry Teacher Compensation Report (lmi.mt.gov/publications)")
} else {
  message("MT DLI teacher compensation fetch failed -- leaving salarymap2.csv's salary columns untouched this run.")
}

if (nrow(teacher_fte) > 0) {
  salarymap2 <- salarymap2 %>%
    select(-any_of(c("Teachers_Total_FTE", "Enrollment", "CCD_Year", "CCD_Source"))) %>%
    left_join(teacher_fte, by = "District") %>%
    mutate(CCD_Source = "NCES Common Core of Data via Urban Institute Education Data Portal (educationdata.urban.org)")
} else {
  message("CCD teacher FTE fetch failed -- leaving salarymap2.csv's staffing columns untouched this run.")
}

write.csv(salarymap2, salarymap2_path, row.names = FALSE)
```

### K-12 county-level context (income, rent, mining/energy employment share, population trend) and district-level child poverty rate, from the Census Bureau
```{r k12 census county and district context, message=FALSE, warning=FALSE, echo=TRUE}
library(dplyr)
source("scrape_helpers.R")
source("census_acs_scraper.R")
source("census_saipe_scraper.R")

# CENSUS_API_KEY must be set (a GitHub Actions secret in CI, .Renviron
# locally). safe_scrape() catches a missing/invalid key the same way it
# catches any other fetch failure: logs it, leaves salarymap2.csv untouched
# this run, rather than crashing the whole pipeline.
county_context <- safe_scrape(
  "Census ACS county context (MT)",
  scrape_fn = fetch_census_county_context,
  expected_cols = c("County", "Median_Household_Income", "Median_Gross_Rent",
                     "Population", "ACS_Year", "Mining_Employment_Share", "Population_Change_Pct")
)

if (nrow(county_context) > 0) {
  salarymap2 <- read.csv(salarymap2_path, fileEncoding = "UTF-8") %>%
    select(-any_of(c("Median_Household_Income", "Median_Gross_Rent", "Population",
                      "ACS_Year", "Mining_Employment_Share", "Population_Change_Pct"))) %>%
    left_join(county_context, by = "County")
  write.csv(salarymap2, salarymap2_path, row.names = FALSE)
} else {
  message("Census ACS county context fetch failed -- leaving salarymap2.csv untouched this run.")
}

child_poverty <- safe_scrape(
  "Census SAIPE district child poverty rate (MT)",
  scrape_fn = fetch_census_saipe_child_poverty,
  expected_cols = c("District", "Child_Poverty_Rate", "SAIPE_Year")
)

if (nrow(child_poverty) > 0) {
  salarymap2 <- read.csv(salarymap2_path, fileEncoding = "UTF-8") %>%
    select(-any_of(c("Child_Poverty_Rate", "SAIPE_Year"))) %>%
    left_join(child_poverty, by = "District")
  write.csv(salarymap2, salarymap2_path, row.names = FALSE)
} else {
  message("Census SAIPE child poverty fetch failed -- leaving salarymap2.csv untouched this run.")
}
```


## Part 2: Montana Higher Ed Data

### HE institutions scraped directly (PeopleAdmin, JazzHR, Paycom)
```{r he direct-platform institutions, message=FALSE, warning=FALSE, echo=TRUE}
library(dplyr)
source("scrape_helpers.R")
source("direct_api_scrapers.R")

he_registry <- read.csv("he_institution_registry.csv", stringsAsFactors = FALSE)

peopleadmin_institutions <- he_registry[he_registry$Platform == "PeopleAdmin", ]
peopleadmin_results <- lapply(seq_len(nrow(peopleadmin_institutions)), function(i) {
  row <- peopleadmin_institutions[i, ]
  df <- safe_scrape(
    row$Institution,
    scrape_fn = function() fetch_peopleadmin_atom(row$Feed_URL, location_fallback = row$Institution),
    expected_cols = c("Title", "Location", "Posted_Date", "Link")
  )
  if (nrow(df) > 0) df$Institution <- row$Institution
  df
})
peopleadmin_df <- bind_rows(peopleadmin_results)

jazzhr_institutions <- he_registry[he_registry$Platform == "JazzHR", ]
jazzhr_results <- lapply(seq_len(nrow(jazzhr_institutions)), function(i) {
  row <- jazzhr_institutions[i, ]
  df <- safe_scrape(
    row$Institution,
    scrape_fn = function() fetch_jazzhr_postings(row$Feed_URL, row$Institution),
    expected_cols = c("Title", "Location", "Posted_Date", "Link")
  )
  if (nrow(df) > 0) df$Institution <- row$Institution
  df
})
jazzhr_df <- bind_rows(jazzhr_results)

paycom_institutions <- he_registry[he_registry$Platform == "Paycom", ]
paycom_results <- lapply(seq_len(nrow(paycom_institutions)), function(i) {
  row <- paycom_institutions[i, ]
  df <- safe_scrape(
    row$Institution,
    scrape_fn = function() fetch_paycom_postings(row$Feed_URL, row$Institution),
    expected_cols = c("Title", "Location", "Posted_Date", "Link")
  )
  if (nrow(df) > 0) df$Institution <- row$Institution
  df
})
paycom_df <- bind_rows(paycom_results)

hedata_raw <- bind_rows(peopleadmin_df, jazzhr_df, paycom_df)
```

### Combine all HE data, classify, archive, and accumulate history
```{r munge he data, message=FALSE, warning=FALSE, echo=TRUE}
library(dplyr)
library(writexl)

hedata <- hedata_raw %>%
  select(Title, Location, Posted_Date, Institution, Link) %>%
  mutate(Posted_Date = as.character(Posted_Date),
         Archive_Date = Sys.Date())

if (!dir.exists("Archived_HE_Data")) dir.create("Archived_HE_Data")
if (!dir.exists("Mt_Ed_Jobs")) dir.create("Mt_Ed_Jobs")

file_name <- paste0("hedata_", Sys.Date(), ".xlsx")
write_xlsx(hedata, path = file.path("Archived_HE_Data", file_name))
write_xlsx(hedata, path = file.path("Mt_Ed_Jobs", "hedata.xlsx"))

# Fix historical institution-name typos before anything downstream keys off
# Institution -- applied AFTER the xlsx archive writes above, so the
# archived raw snapshot keeps whatever spelling the scraper actually
# produced that week.
hedata <- hedata %>% mutate(Institution = canonicalize_he_institution(Institution))

this_week_he_cat <- hedata %>% mutate(Job_Type = classify_he_job_type(Title))
this_week_facultydata <- this_week_he_cat %>%
  filter(Job_Type %in% c("Instructor/Teacher/Faculty", "Adjunct/Part-Time Faculty")) %>%
  mutate(Category = classify_he_faculty_category(Title))

source("history_accumulator.R")

facultydata <- append_weekly_rows(file.path("Mt_Ed_Jobs", "facultydata.csv"), as.data.frame(this_week_facultydata))
write.csv(facultydata, file.path("Mt_Ed_Jobs", "facultydata.csv"), row.names = FALSE)

this_week_he_totals <- hedata %>%
  count(Institution, Archive_Date, name = "n")
he_institution_weekly_totals <- append_weekly_rows(
  file.path("Mt_Ed_Jobs", "he_institution_weekly_totals.csv"), this_week_he_totals)
write.csv(he_institution_weekly_totals, file.path("Mt_Ed_Jobs", "he_institution_weekly_totals.csv"), row.names = FALSE)

this_week_hesum <- this_week_facultydata %>%
  group_by(Category, Archive_Date, Job_Type) %>%
  summarize(sum = n(), .groups = "drop") %>%
  mutate(Institution = "Total") %>%
  select(Category, Archive_Date, Institution, Job_Type, sum)

this_week_hesuminst <- this_week_facultydata %>%
  group_by(Category, Archive_Date, Institution, Job_Type) %>%
  summarise(sum = n(), .groups = "drop")

check_total_matches_parts(this_week_hesum, this_week_hesuminst,
                           group_cols = c("Category", "Archive_Date", "Job_Type"))

this_week_allsum_he <- bind_rows(this_week_hesum, this_week_hesuminst)
Allsum_he <- append_weekly_rows(file.path("Mt_Ed_Jobs", "allsum_he.csv"), this_week_allsum_he)
write.csv(Allsum_he, file = file.path("Mt_Ed_Jobs", "allsum_he.csv"), row.names = FALSE)

henowsum <- this_week_hesum %>%
  ungroup() %>%
  rename(Sum = sum) %>%
  select(Category, Job_Type, Sum, Institution)

henowinstsum <- this_week_facultydata %>%
  group_by(Category, Institution, Job_Type) %>%
  summarize(Sum = n(), .groups = "drop") %>%
  select(Category, Sum, Institution, Job_Type)

Allnow_he <- bind_rows(henowsum, henowinstsum)
write.csv(Allnow_he, file = file.path("Mt_Ed_Jobs", "allnow_he.csv"), row.names = FALSE)
```

### HE faculty salary, enrollment, and Pell Grant recipient share (IPEDS via Urban Institute)
```{r he salary enrollment pell data, message=FALSE, warning=FALSE, echo=TRUE}
library(dplyr)
source("scrape_helpers.R")
source("ipeds_salary_scraper.R")
source("ipeds_enrollment_scraper.R")
source("fsa_pell_scraper.R")

he_salary <- safe_scrape(
  "IPEDS instructional staff salaries (MT)",
  scrape_fn = fetch_ipeds_he_salaries,
  expected_cols = c("Name", "Faculty_Avg_Salary", "Faculty_Avg_Salary_Professor",
                     "Faculty_Count", "Salary_Year")
)

he_enrollment <- safe_scrape(
  "IPEDS fall enrollment FTE (MT)",
  scrape_fn = fetch_ipeds_he_enrollment,
  expected_cols = c("Name", "Enrollment", "Enrollment_Year")
)

he_enrollment_trend <- safe_scrape(
  "IPEDS fall enrollment 5-year trend (MT)",
  scrape_fn = fetch_ipeds_he_enrollment_trend,
  expected_cols = c("Name", "Enrollment_Change_Pct")
)

he_pell_share <- safe_scrape(
  "FSA Pell Grant recipient share (MT)",
  scrape_fn = fetch_ipeds_he_pell_share,
  expected_cols = c("Name", "Pell_Recipient_Share", "Pell_Year")
)

# Static geo/link fields (Name/County/Latitude/Longitude/Link) come from
# he_institution_registry.csv, the same "read salarymap.csv back first if
# it exists, don't blank out a failed fetch's columns" pattern
# salarymap2.csv's chunk above uses.
he_registry <- read.csv("he_institution_registry.csv", stringsAsFactors = FALSE) %>%
  transmute(Name = Institution, County, Longitude, Latitude, Link = Job_Link)

salarymap_path <- file.path("Mt_Ed_Jobs", "salarymap.csv")
salarymap <- if (file.exists(salarymap_path)) {
  read.csv(salarymap_path, fileEncoding = "UTF-8") %>%
    select(-any_of(c("County", "Longitude", "Latitude", "Link"))) %>%
    right_join(he_registry, by = "Name") %>%
    select(Name, County, Longitude, Latitude, Link, everything())
} else {
  he_registry
}

if (nrow(he_salary) > 0) {
  salarymap <- salarymap %>%
    select(-any_of(c("Faculty_Avg_Salary", "Faculty_Avg_Salary_Professor",
                      "Faculty_Count", "Salary_Year", "Salary_Source"))) %>%
    left_join(he_salary, by = "Name") %>%
    mutate(Salary_Source = "IPEDS via Urban Institute Education Data Portal (educationdata.urban.org)")
} else {
  message("IPEDS salary fetch failed -- leaving salarymap.csv's salary columns untouched this run.")
}

if (nrow(he_enrollment) > 0) {
  salarymap <- salarymap %>%
    select(-any_of(c("Enrollment", "Enrollment_Year"))) %>%
    left_join(he_enrollment, by = "Name")
} else {
  message("IPEDS fall enrollment fetch failed -- leaving salarymap.csv's Enrollment untouched this run.")
}

if (nrow(he_enrollment_trend) > 0) {
  salarymap <- salarymap %>%
    select(-any_of("Enrollment_Change_Pct")) %>%
    left_join(he_enrollment_trend, by = "Name")
} else {
  message("IPEDS fall enrollment trend fetch failed -- leaving salarymap.csv's Enrollment_Change_Pct untouched this run.")
}

if (nrow(he_pell_share) > 0) {
  salarymap <- salarymap %>%
    select(-any_of(c("Pell_Recipient_Share", "Pell_Year"))) %>%
    left_join(he_pell_share, by = "Name")
} else {
  message("FSA Pell Grant recipient share fetch failed -- leaving salarymap.csv's Pell columns untouched this run.")
}

write.csv(salarymap, salarymap_path, row.names = FALSE)
```

### HE institution county-level context (income, rent, mining/energy employment share, population trend), from the Census Bureau
```{r he census county context, message=FALSE, warning=FALSE, echo=TRUE}
library(dplyr)
source("scrape_helpers.R")
source("census_acs_scraper.R")

# Reuses the exact same fetch_census_county_context() pipeline as the K-12
# chunk earlier in this file -- fetched independently rather than reusing
# that chunk's `county_context` variable, matching every other chunk in
# this file being self-contained and re-runnable on its own.
county_context_he <- safe_scrape(
  "Census ACS county context for HE institutions (MT)",
  scrape_fn = fetch_census_county_context,
  expected_cols = c("County", "Median_Household_Income", "Median_Gross_Rent",
                     "Population", "ACS_Year", "Mining_Employment_Share", "Population_Change_Pct")
)

if (nrow(county_context_he) > 0) {
  salarymap <- read.csv(salarymap_path, fileEncoding = "UTF-8") %>%
    select(-any_of(c("Median_Household_Income", "Median_Gross_Rent", "Population",
                      "ACS_Year", "Mining_Employment_Share", "Population_Change_Pct"))) %>%
    left_join(county_context_he, by = "County")
  write.csv(salarymap, salarymap_path, row.names = FALSE)
} else {
  message("Census ACS county context fetch failed -- leaving salarymap.csv untouched this run.")
}
```
