---
title: "MT Job Scrape"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("k12_he_classification.R")
```
# Scrapes Montana's K-12 and higher-ed job postings, salary, and staffing data and combines them into the datasets
# Mt_Ed_Jobs/app.R reads. Mirrors the Wyoming Education Jobs Dashboard's Wy_ED_Jobs.Rmd.

## Part 1: Montana K-12 Data

### K-12 districts scraped directly (AppliTrack, SchoolSpring, Tyler Portico, TedK12)
```{r k12 direct-platform districts, message=FALSE, warning=FALSE, echo=TRUE}
library(dplyr)
library(readr)
library(chromote)
source("scrape_helpers.R")
source("direct_api_scrapers.R")
source("misc_district_scrapers.R")

registry <- read.csv("k12_district_registry.csv", stringsAsFactors = FALSE)

# AppliTrack -- output columns (title/position/position2/date_posted/
# location/closing_date) already match combinedclean's shape closely; only
# District needs adding.
applitrack_districts <- registry[registry$Platform == "AppliTrack", ]
applitrack_results <- lapply(seq_len(nrow(applitrack_districts)), function(i) {
  row <- applitrack_districts[i, ]
  df <- safe_scrape(
    row$District,
    scrape_fn = function() fetch_applitrack_postings(row$Slug),
    expected_cols = c("title", "position", "position2", "date_posted", "location", "closing_date")
  )
  if (nrow(df) > 0) df$District <- row$District
  df
})
# url comes from a join back to the registry (one job-board URL per
# district, matching every other source's convention -- not a per-posting
# deep link) since AppliTrack's own fetch doesn't carry the district's URL
# through per-row.
applitrack_df <- bind_rows(applitrack_results) %>%
  left_join(select(applitrack_districts, District, Job_Link), by = "District") %>%
  transmute(title, date_posted, position = NA_character_, location, url = Job_Link, District,
            Posting_Source = "AppliTrack (direct district board)")

# SchoolSpring / Tyler Portico -- same output shape (Title/Location/
# Posted_Date/Link), position is always recomputed from title downstream so
# it's set NA_character_ here rather than kept from the source (matching
# Wyoming's springer/SchoolSpring chunk's own convention).
schoolspring_districts <- registry[registry$Platform == "SchoolSpring", ]
schoolspring_results <- lapply(seq_len(nrow(schoolspring_districts)), function(i) {
  row <- schoolspring_districts[i, ]
  df <- safe_scrape(
    row$District,
    scrape_fn = function() fetch_schoolspring_postings(row$Slug),
    expected_cols = c("Title", "Location", "Posted_Date", "Link")
  )
  if (nrow(df) > 0) df$District <- row$District
  df
})
schoolspring_df <- bind_rows(schoolspring_results)
if (nrow(schoolspring_df) > 0) {
  schoolspring_df <- schoolspring_df %>%
    transmute(title = Title, date_posted = Posted_Date, position = NA_character_,
              location = Location, url = Link, District,
              Posting_Source = "SchoolSpring (direct district board)")
} else {
  schoolspring_df <- data.frame(title = character(0), date_posted = character(0), position = character(0),
                                 location = character(0), url = character(0), District = character(0),
                                 Posting_Source = character(0))
}

tylerportico_districts <- registry[registry$Platform == "TylerPortico", ]
tylerportico_results <- lapply(seq_len(nrow(tylerportico_districts)), function(i) {
  row <- tylerportico_districts[i, ]
  df <- safe_scrape(
    row$District,
    scrape_fn = function() fetch_tylerportico_postings(row$Slug, row$District),
    expected_cols = c("Title", "Location", "Posted_Date", "Link")
  )
  if (nrow(df) > 0) df$District <- row$District
  df
})
tylerportico_df <- bind_rows(tylerportico_results)
if (nrow(tylerportico_df) > 0) {
  tylerportico_df <- tylerportico_df %>%
    transmute(title = Title, date_posted = Posted_Date, position = NA_character_,
              location = Location, url = Link, District,
              Posting_Source = "Tyler Portico (direct district board)")
} else {
  tylerportico_df <- data.frame(title = character(0), date_posted = character(0), position = character(0),
                                 location = character(0), url = character(0), District = character(0),
                                 Posting_Source = character(0))
}

# TedK12 -- output columns (title/date_posted/position/location/url) already
# match combinedclean's shape; only District needs adding.
tedk12_districts <- registry[registry$Platform == "TedK12", ]
tedk12_results <- lapply(seq_len(nrow(tedk12_districts)), function(i) {
  row <- tedk12_districts[i, ]
  df <- safe_scrape(
    row$District,
    scrape_fn = function() fetch_tedk12_postings(row$Slug),
    expected_cols = c("title", "date_posted", "position", "location", "url")
  )
  if (nrow(df) > 0) df$District <- row$District
  df
})
tedk12_df <- bind_rows(tedk12_results)
if (nrow(tedk12_df) == 0) {
  tedk12_df <- data.frame(title = character(0), date_posted = character(0), position = character(0),
                           location = character(0), url = character(0), District = character(0),
                           Posting_Source = character(0))
} else {
  tedk12_df <- tedk12_df %>%
    mutate(Posting_Source = "TedK12 (direct district board)")
}

# Livingston and Lodge Grass have no structured ATS -- heuristic scrapers
# in misc_district_scrapers.R read their own site's real page structure
# directly, same acknowledged-less-reliable-source spirit as
# misc_college_scrapers.R on the HE side.
livingston_districts <- registry[registry$Platform == "LivingstonHeuristic", ]
livingston_results <- lapply(seq_len(nrow(livingston_districts)), function(i) {
  row <- livingston_districts[i, ]
  df <- safe_scrape(
    row$District,
    scrape_fn = function() fetch_livingston_postings(row$Job_Link),
    expected_cols = c("Title", "Location", "Posted_Date", "Link")
  )
  if (nrow(df) > 0) df$District <- row$District
  df
})
livingston_df <- bind_rows(livingston_results)
if (nrow(livingston_df) > 0) {
  livingston_df <- livingston_df %>%
    transmute(title = Title, date_posted = Posted_Date, position = NA_character_,
              location = Location, url = Link, District,
              Posting_Source = "Livingston district site (direct board)")
} else {
  livingston_df <- data.frame(title = character(0), date_posted = character(0), position = character(0),
                               location = character(0), url = character(0), District = character(0),
                               Posting_Source = character(0))
}

lodgegrass_districts <- registry[registry$Platform == "LodgeGrassHeuristic", ]
lodgegrass_results <- lapply(seq_len(nrow(lodgegrass_districts)), function(i) {
  row <- lodgegrass_districts[i, ]
  df <- safe_scrape(
    row$District,
    scrape_fn = function() fetch_lodgegrass_postings(row$Job_Link),
    expected_cols = c("Title", "Location", "Posted_Date", "Link")
  )
  if (nrow(df) > 0) df$District <- row$District
  df
})
lodgegrass_df <- bind_rows(lodgegrass_results)
if (nrow(lodgegrass_df) > 0) {
  lodgegrass_df <- lodgegrass_df %>%
    transmute(title = Title, date_posted = Posted_Date, position = NA_character_,
              location = Location, url = Link, District,
              Posting_Source = "Lodge Grass district site (direct board)")
} else {
  lodgegrass_df <- data.frame(title = character(0), date_posted = character(0), position = character(0),
                               location = character(0), url = character(0), District = character(0),
                               Posting_Source = character(0))
}

# Broadview has no structured ATS either -- same "Educational Networks" CMS
# as Livingston/Lodge Grass but split across 4 real pages instead of 1 (see
# misc_district_scrapers.R's own comment for the real page-by-page layout).
# fetch_broadview_postings() takes no row/url argument (unlike
# fetch_livingston_postings()/fetch_lodgegrass_postings()) since its 4 real
# page URLs are hardcoded internally -- the registry's Job_Link is only the
# hub page, not a fetchable single feed.
broadview_districts <- registry[registry$Platform == "BroadviewHeuristic", ]
broadview_results <- lapply(seq_len(nrow(broadview_districts)), function(i) {
  row <- broadview_districts[i, ]
  df <- safe_scrape(
    row$District,
    scrape_fn = function() fetch_broadview_postings(),
    expected_cols = c("Title", "Location", "Posted_Date", "Link")
  )
  if (nrow(df) > 0) df$District <- row$District
  df
})
broadview_df <- bind_rows(broadview_results)
if (nrow(broadview_df) > 0) {
  broadview_df <- broadview_df %>%
    transmute(title = Title, date_posted = Posted_Date, position = NA_character_,
              location = Location, url = Link, District,
              Posting_Source = "Broadview district site (direct board)")
} else {
  broadview_df <- data.frame(title = character(0), date_posted = character(0), position = character(0),
                              location = character(0), url = character(0), District = character(0),
                              Posting_Source = character(0))
}

# Custer genuinely runs Finalsite (unlike every other district in the same
# 2026-08-16 pass, which turned out to be Apptegy despite an initial
# "Finalsite cluster" hypothesis) -- a plain httr2 fetch, no chromote
# needed, same pattern as Livingston/Lodge Grass/Broadview above.
custer_districts <- registry[registry$Platform == "CusterHeuristic", ]
custer_results <- lapply(seq_len(nrow(custer_districts)), function(i) {
  row <- custer_districts[i, ]
  df <- safe_scrape(
    row$District,
    scrape_fn = function() fetch_custer_postings(row$Job_Link),
    expected_cols = c("Title", "Location", "Posted_Date", "Link")
  )
  if (nrow(df) > 0) df$District <- row$District
  df
})
custer_df <- bind_rows(custer_results)
if (nrow(custer_df) > 0) {
  custer_df <- custer_df %>%
    transmute(title = Title, date_posted = Posted_Date, position = NA_character_,
              location = Location, url = Link, District,
              Posting_Source = "Custer district site (direct board)")
} else {
  custer_df <- data.frame(title = character(0), date_posted = character(0), position = character(0),
                           location = character(0), url = character(0), District = character(0),
                           Posting_Source = character(0))
}

# Scobey (a Weebly site, found 2026-08-16 -- the single highest-volume
# OPI-only location left) also has no structured ATS -- a plain httr2
# fetch, no chromote needed, same pattern as Custer above.
scobey_districts <- registry[registry$Platform == "ScobeyHeuristic", ]
scobey_results <- lapply(seq_len(nrow(scobey_districts)), function(i) {
  row <- scobey_districts[i, ]
  df <- safe_scrape(
    row$District,
    scrape_fn = function() fetch_scobey_postings(row$Job_Link),
    expected_cols = c("Title", "Location", "Posted_Date", "Link")
  )
  if (nrow(df) > 0) df$District <- row$District
  df
})
scobey_df <- bind_rows(scobey_results)
if (nrow(scobey_df) > 0) {
  scobey_df <- scobey_df %>%
    transmute(title = Title, date_posted = Posted_Date, position = NA_character_,
              location = Location, url = Link, District,
              Posting_Source = "Scobey district site (direct board)")
} else {
  scobey_df <- data.frame(title = character(0), date_posted = character(0), position = character(0),
                           location = character(0), url = character(0), District = character(0),
                           Posting_Source = character(0))
}

# Ramsay (a plain WordPress site, found 2026-08-23) also has no structured
# ATS -- a plain httr2 fetch, no chromote needed, same pattern as Custer/
# Scobey above.
ramsay_districts <- registry[registry$Platform == "RamsayHeuristic", ]
ramsay_results <- lapply(seq_len(nrow(ramsay_districts)), function(i) {
  row <- ramsay_districts[i, ]
  df <- safe_scrape(
    row$District,
    scrape_fn = function() fetch_ramsay_postings(row$Job_Link),
    expected_cols = c("Title", "Location", "Posted_Date", "Link")
  )
  if (nrow(df) > 0) df$District <- row$District
  df
})
ramsay_df <- bind_rows(ramsay_results)
if (nrow(ramsay_df) > 0) {
  ramsay_df <- ramsay_df %>%
    transmute(title = Title, date_posted = Posted_Date, position = NA_character_,
              location = Location, url = Link, District,
              Posting_Source = "Ramsay district site (direct board)")
} else {
  ramsay_df <- data.frame(title = character(0), date_posted = character(0), position = character(0),
                           location = character(0), url = character(0), District = character(0),
                           Posting_Source = character(0))
}

# Roy (a plain Joomla site, found 2026-08-23) also has no structured ATS --
# a plain httr2 fetch, no chromote needed, same pattern as Custer/Scobey/
# Ramsay above.
roy_districts <- registry[registry$Platform == "RoyHeuristic", ]
roy_results <- lapply(seq_len(nrow(roy_districts)), function(i) {
  row <- roy_districts[i, ]
  df <- safe_scrape(
    row$District,
    scrape_fn = function() fetch_roy_postings(row$Job_Link),
    expected_cols = c("Title", "Location", "Posted_Date", "Link")
  )
  if (nrow(df) > 0) df$District <- row$District
  df
})
roy_df <- bind_rows(roy_results)
if (nrow(roy_df) > 0) {
  roy_df <- roy_df %>%
    transmute(title = Title, date_posted = Posted_Date, position = NA_character_,
              location = Location, url = Link, District,
              Posting_Source = "Roy district site (direct board)")
} else {
  roy_df <- data.frame(title = character(0), date_posted = character(0), position = character(0),
                        location = character(0), url = character(0), District = character(0),
                        Posting_Source = character(0))
}

# Arrowhead (a modern WordPress/Divi site, found 2026-08-23) also has no
# structured ATS -- a plain httr2 fetch, no chromote needed, same pattern
# as Custer/Scobey/Ramsay/Roy above (its own fetch_arrowhead_postings()
# uses a different, site-required User-Agent internally -- see that
# function's own comment).
arrowhead_districts <- registry[registry$Platform == "ArrowheadHeuristic", ]
arrowhead_results <- lapply(seq_len(nrow(arrowhead_districts)), function(i) {
  row <- arrowhead_districts[i, ]
  df <- safe_scrape(
    row$District,
    scrape_fn = function() fetch_arrowhead_postings(row$Job_Link),
    expected_cols = c("Title", "Location", "Posted_Date", "Link")
  )
  if (nrow(df) > 0) df$District <- row$District
  df
})
arrowhead_df <- bind_rows(arrowhead_results)
if (nrow(arrowhead_df) > 0) {
  arrowhead_df <- arrowhead_df %>%
    transmute(title = Title, date_posted = Posted_Date, position = NA_character_,
              location = Location, url = Link, District,
              Posting_Source = "Arrowhead district site (direct board)")
} else {
  arrowhead_df <- data.frame(title = character(0), date_posted = character(0), position = character(0),
                              location = character(0), url = character(0), District = character(0),
                              Posting_Source = character(0))
}

# North Star (a publicly published Google Sites page, found 2026-08-23,
# serving both Rudyard and Gildford) also has no structured ATS -- a plain
# httr2 fetch, no chromote needed, same pattern as Custer/Scobey/Ramsay/
# Roy/Arrowhead above.
northstar_districts <- registry[registry$Platform == "NorthStarHeuristic", ]
northstar_results <- lapply(seq_len(nrow(northstar_districts)), function(i) {
  row <- northstar_districts[i, ]
  df <- safe_scrape(
    row$District,
    scrape_fn = function() fetch_northstar_postings(row$Job_Link),
    expected_cols = c("Title", "Location", "Posted_Date", "Link")
  )
  if (nrow(df) > 0) df$District <- row$District
  df
})
northstar_df <- bind_rows(northstar_results)
if (nrow(northstar_df) > 0) {
  northstar_df <- northstar_df %>%
    transmute(title = Title, date_posted = Posted_Date, position = NA_character_,
              location = Location, url = Link, District,
              Posting_Source = "North Star district site (direct board)")
} else {
  northstar_df <- data.frame(title = character(0), date_posted = character(0), position = character(0),
                              location = character(0), url = character(0), District = character(0),
                              Posting_Source = character(0))
}

# Shields Valley (genuinely Finalsite, found 2026-08-23, serving both
# Clyde Park and Wilsall) also has no structured ATS -- a plain httr2
# fetch, no chromote needed, same pattern as Custer/Scobey/Ramsay/Roy/
# Arrowhead/North Star above.
shieldsvalley_districts <- registry[registry$Platform == "ShieldsValleyHeuristic", ]
shieldsvalley_results <- lapply(seq_len(nrow(shieldsvalley_districts)), function(i) {
  row <- shieldsvalley_districts[i, ]
  df <- safe_scrape(
    row$District,
    scrape_fn = function() fetch_shieldsvalley_postings(row$Job_Link),
    expected_cols = c("Title", "Location", "Posted_Date", "Link")
  )
  if (nrow(df) > 0) df$District <- row$District
  df
})
shieldsvalley_df <- bind_rows(shieldsvalley_results)
if (nrow(shieldsvalley_df) > 0) {
  shieldsvalley_df <- shieldsvalley_df %>%
    transmute(title = Title, date_posted = Posted_Date, position = NA_character_,
              location = Location, url = Link, District,
              Posting_Source = "Shields Valley district site (direct board)")
} else {
  shieldsvalley_df <- data.frame(title = character(0), date_posted = character(0), position = character(0),
                                  location = character(0), url = character(0), District = character(0),
                                  Posting_Source = character(0))
}

# Thompson Falls (genuinely Finalsite, found 2026-08-23) also has no
# structured ATS -- a plain httr2 fetch, no chromote needed, same pattern
# as Custer/Scobey/Ramsay/Roy/Arrowhead/North Star/Shields Valley above.
thompsonfalls_districts <- registry[registry$Platform == "ThompsonFallsHeuristic", ]
thompsonfalls_results <- lapply(seq_len(nrow(thompsonfalls_districts)), function(i) {
  row <- thompsonfalls_districts[i, ]
  df <- safe_scrape(
    row$District,
    scrape_fn = function() fetch_thompsonfalls_postings(row$Job_Link),
    expected_cols = c("Title", "Location", "Posted_Date", "Link")
  )
  if (nrow(df) > 0) df$District <- row$District
  df
})
thompsonfalls_df <- bind_rows(thompsonfalls_results)
if (nrow(thompsonfalls_df) > 0) {
  thompsonfalls_df <- thompsonfalls_df %>%
    transmute(title = Title, date_posted = Posted_Date, position = NA_character_,
              location = Location, url = Link, District,
              Posting_Source = "Thompson Falls district site (direct board)")
} else {
  thompsonfalls_df <- data.frame(title = character(0), date_posted = character(0), position = character(0),
                                  location = character(0), url = character(0), District = character(0),
                                  Posting_Source = character(0))
}

# Ekalaka (a real Job Postings module, found 2026-08-23) also has no
# structured ATS in this project's own platform list -- a plain httr2
# fetch, no chromote needed, same pattern as Custer/Scobey/Ramsay/Roy/
# Arrowhead/North Star/Shields Valley/Thompson Falls above.
ekalaka_districts <- registry[registry$Platform == "EkalakaHeuristic", ]
ekalaka_results <- lapply(seq_len(nrow(ekalaka_districts)), function(i) {
  row <- ekalaka_districts[i, ]
  df <- safe_scrape(
    row$District,
    scrape_fn = function() fetch_ekalaka_postings(row$Job_Link),
    expected_cols = c("Title", "Location", "Posted_Date", "Link")
  )
  if (nrow(df) > 0) df$District <- row$District
  df
})
ekalaka_df <- bind_rows(ekalaka_results)
if (nrow(ekalaka_df) > 0) {
  ekalaka_df <- ekalaka_df %>%
    transmute(title = Title, date_posted = Posted_Date, position = NA_character_,
              location = Location, url = Link, District,
              Posting_Source = "Ekalaka district site (direct board)")
} else {
  ekalaka_df <- data.frame(title = character(0), date_posted = character(0), position = character(0),
                            location = character(0), url = character(0), District = character(0),
                            Posting_Source = character(0))
}

# Trego School District 53 (a publicly published Google Sites page, found
# 2026-08-24) also has no structured ATS -- a plain httr2 fetch, no
# chromote needed, same pattern as Custer/Scobey/Ramsay/Roy/Arrowhead/
# North Star/Shields Valley/Thompson Falls/Ekalaka above.
trego_districts <- registry[registry$Platform == "TregoHeuristic", ]
trego_results <- lapply(seq_len(nrow(trego_districts)), function(i) {
  row <- trego_districts[i, ]
  df <- safe_scrape(
    row$District,
    scrape_fn = function() fetch_trego_postings(row$Job_Link),
    expected_cols = c("Title", "Location", "Posted_Date", "Link")
  )
  if (nrow(df) > 0) df$District <- row$District
  df
})
trego_df <- bind_rows(trego_results)
if (nrow(trego_df) > 0) {
  trego_df <- trego_df %>%
    transmute(title = Title, date_posted = Posted_Date, position = NA_character_,
              location = Location, url = Link, District,
              Posting_Source = "Trego district site (direct board)")
} else {
  trego_df <- data.frame(title = character(0), date_posted = character(0), position = character(0),
                          location = character(0), url = character(0), District = character(0),
                          Posting_Source = character(0))
}

# Baker Public Schools (Finalsite, found 2026-08-24) also has no
# structured ATS -- a plain httr2 fetch, no chromote needed, same
# pattern as Thompson Falls/Hobson/Shepherd above.
baker_districts <- registry[registry$Platform == "BakerHeuristic", ]
baker_results <- lapply(seq_len(nrow(baker_districts)), function(i) {
  row <- baker_districts[i, ]
  df <- safe_scrape(
    row$District,
    scrape_fn = function() fetch_baker_postings(row$Job_Link),
    expected_cols = c("Title", "Location", "Posted_Date", "Link")
  )
  if (nrow(df) > 0) df$District <- row$District
  df
})
baker_df <- bind_rows(baker_results)
if (nrow(baker_df) > 0) {
  baker_df <- baker_df %>%
    transmute(title = Title, date_posted = Posted_Date, position = NA_character_,
              location = Location, url = Link, District,
              Posting_Source = "Baker district site (direct board)")
} else {
  baker_df <- data.frame(title = character(0), date_posted = character(0), position = character(0),
                          location = character(0), url = character(0), District = character(0),
                          Posting_Source = character(0))
}

# Cut Bank School District #15 (a publicly published Google Sites page,
# found 2026-08-24) also has no structured ATS -- a plain httr2 fetch,
# no chromote needed, same pattern as the other heuristic districts
# above.
cutbank_districts <- registry[registry$Platform == "CutBankHeuristic", ]
cutbank_results <- lapply(seq_len(nrow(cutbank_districts)), function(i) {
  row <- cutbank_districts[i, ]
  df <- safe_scrape(
    row$District,
    scrape_fn = function() fetch_cutbank_postings(row$Job_Link),
    expected_cols = c("Title", "Location", "Posted_Date", "Link")
  )
  if (nrow(df) > 0) df$District <- row$District
  df
})
cutbank_df <- bind_rows(cutbank_results)
if (nrow(cutbank_df) > 0) {
  cutbank_df <- cutbank_df %>%
    transmute(title = Title, date_posted = Posted_Date, position = NA_character_,
              location = Location, url = Link, District,
              Posting_Source = "Cut Bank district site (direct board)")
} else {
  cutbank_df <- data.frame(title = character(0), date_posted = character(0), position = character(0),
                            location = character(0), url = character(0), District = character(0),
                            Posting_Source = character(0))
}

# Hinsdale Public Schools (an unbranded CMS, found 2026-08-24) also has
# no structured ATS -- a plain httr2 fetch, no chromote needed, same
# pattern as the other heuristic districts above.
hinsdale_districts <- registry[registry$Platform == "HinsdaleHeuristic", ]
hinsdale_results <- lapply(seq_len(nrow(hinsdale_districts)), function(i) {
  row <- hinsdale_districts[i, ]
  df <- safe_scrape(
    row$District,
    scrape_fn = function() fetch_hinsdale_postings(row$Job_Link),
    expected_cols = c("Title", "Location", "Posted_Date", "Link")
  )
  if (nrow(df) > 0) df$District <- row$District
  df
})
hinsdale_df <- bind_rows(hinsdale_results)
if (nrow(hinsdale_df) > 0) {
  hinsdale_df <- hinsdale_df %>%
    transmute(title = Title, date_posted = Posted_Date, position = NA_character_,
              location = Location, url = Link, District,
              Posting_Source = "Hinsdale district site (direct board)")
} else {
  hinsdale_df <- data.frame(title = character(0), date_posted = character(0), position = character(0),
                             location = character(0), url = character(0), District = character(0),
                             Posting_Source = character(0))
}

# Valier School District #18 (a publicly published Google Sites page,
# found 2026-08-24) also has no structured ATS -- a plain httr2 fetch,
# no chromote needed, same pattern as the other heuristic districts
# above.
valier_districts <- registry[registry$Platform == "ValierHeuristic", ]
valier_results <- lapply(seq_len(nrow(valier_districts)), function(i) {
  row <- valier_districts[i, ]
  df <- safe_scrape(
    row$District,
    scrape_fn = function() fetch_valier_postings(row$Job_Link),
    expected_cols = c("Title", "Location", "Posted_Date", "Link")
  )
  if (nrow(df) > 0) df$District <- row$District
  df
})
valier_df <- bind_rows(valier_results)
if (nrow(valier_df) > 0) {
  valier_df <- valier_df %>%
    transmute(title = Title, date_posted = Posted_Date, position = NA_character_,
              location = Location, url = Link, District,
              Posting_Source = "Valier district site (direct board)")
} else {
  valier_df <- data.frame(title = character(0), date_posted = character(0), position = character(0),
                           location = character(0), url = character(0), District = character(0),
                           Posting_Source = character(0))
}

# Roberts Public School (a Joomla-based CMS, found 2026-08-24) also has
# no structured ATS -- a plain httr2 fetch, no chromote needed, same
# pattern as the other heuristic districts above.
roberts_districts <- registry[registry$Platform == "RobertsHeuristic", ]
roberts_results <- lapply(seq_len(nrow(roberts_districts)), function(i) {
  row <- roberts_districts[i, ]
  df <- safe_scrape(
    row$District,
    scrape_fn = function() fetch_roberts_postings(row$Job_Link),
    expected_cols = c("Title", "Location", "Posted_Date", "Link")
  )
  if (nrow(df) > 0) df$District <- row$District
  df
})
roberts_df <- bind_rows(roberts_results)
if (nrow(roberts_df) > 0) {
  roberts_df <- roberts_df %>%
    transmute(title = Title, date_posted = Posted_Date, position = NA_character_,
              location = Location, url = Link, District,
              Posting_Source = "Roberts district site (direct board)")
} else {
  roberts_df <- data.frame(title = character(0), date_posted = character(0), position = character(0),
                            location = character(0), url = character(0), District = character(0),
                            Posting_Source = character(0))
}

# Winnett Public Schools (Squarespace, found 2026-08-24) also has no
# structured ATS in this project's own platform list -- a plain httr2
# fetch, no chromote needed, same pattern as Terry above.
winnett_districts <- registry[registry$Platform == "WinnettHeuristic", ]
winnett_results <- lapply(seq_len(nrow(winnett_districts)), function(i) {
  row <- winnett_districts[i, ]
  df <- safe_scrape(
    row$District,
    scrape_fn = function() fetch_winnett_postings(row$Job_Link),
    expected_cols = c("Title", "Location", "Posted_Date", "Link")
  )
  if (nrow(df) > 0) df$District <- row$District
  df
})
winnett_df <- bind_rows(winnett_results)
if (nrow(winnett_df) > 0) {
  winnett_df <- winnett_df %>%
    transmute(title = Title, date_posted = Posted_Date, position = NA_character_,
              location = Location, url = Link, District,
              Posting_Source = "Winnett district site (direct board)")
} else {
  winnett_df <- data.frame(title = character(0), date_posted = character(0), position = character(0),
                            location = character(0), url = character(0), District = character(0),
                            Posting_Source = character(0))
}

# Miles City / Custer County District 1 (SCHOOLinSITES CMS, found
# 2026-08-24) publishes jobs on a live Google Sheet instead of any HTML
# page -- a plain httr2 fetch of the sheet's CSV export endpoint, no
# chromote needed.
milescity_districts <- registry[registry$Platform == "MilesCityHeuristic", ]
milescity_results <- lapply(seq_len(nrow(milescity_districts)), function(i) {
  row <- milescity_districts[i, ]
  df <- safe_scrape(
    row$District,
    scrape_fn = function() fetch_milescity_postings(row$Job_Link),
    expected_cols = c("Title", "Location", "Posted_Date", "Link")
  )
  if (nrow(df) > 0) df$District <- row$District
  df
})
milescity_df <- bind_rows(milescity_results)
if (nrow(milescity_df) > 0) {
  milescity_df <- milescity_df %>%
    transmute(title = Title, date_posted = Posted_Date, position = NA_character_,
              location = Location, url = Link, District,
              Posting_Source = "Miles City district site (Google Sheets job board)")
} else {
  milescity_df <- data.frame(title = character(0), date_posted = character(0), position = character(0),
                              location = character(0), url = character(0), District = character(0),
                              Posting_Source = character(0))
}

# Augusta Public School (a Wix site, found 2026-08-24) also has no
# structured ATS -- a plain httr2 fetch, no chromote needed, same
# pattern as the other heuristic districts above.
augusta_districts <- registry[registry$Platform == "AugustaHeuristic", ]
augusta_results <- lapply(seq_len(nrow(augusta_districts)), function(i) {
  row <- augusta_districts[i, ]
  df <- safe_scrape(
    row$District,
    scrape_fn = function() fetch_augusta_postings(row$Job_Link),
    expected_cols = c("Title", "Location", "Posted_Date", "Link")
  )
  if (nrow(df) > 0) df$District <- row$District
  df
})
augusta_df <- bind_rows(augusta_results)
if (nrow(augusta_df) > 0) {
  augusta_df <- augusta_df %>%
    transmute(title = Title, date_posted = Posted_Date, position = NA_character_,
              location = Location, url = Link, District,
              Posting_Source = "Augusta district site (direct board)")
} else {
  augusta_df <- data.frame(title = character(0), date_posted = character(0), position = character(0),
                            location = character(0), url = character(0), District = character(0),
                            Posting_Source = character(0))
}

# Brockton School District (SCHOOLinSITES CMS, found 2026-08-24) also
# has no structured ATS -- a plain httr2 fetch, no chromote needed, same
# pattern as the other heuristic districts above.
brockton_districts <- registry[registry$Platform == "BrocktonHeuristic", ]
brockton_results <- lapply(seq_len(nrow(brockton_districts)), function(i) {
  row <- brockton_districts[i, ]
  df <- safe_scrape(
    row$District,
    scrape_fn = function() fetch_brockton_postings(row$Job_Link),
    expected_cols = c("Title", "Location", "Posted_Date", "Link")
  )
  if (nrow(df) > 0) df$District <- row$District
  df
})
brockton_df <- bind_rows(brockton_results)
if (nrow(brockton_df) > 0) {
  brockton_df <- brockton_df %>%
    transmute(title = Title, date_posted = Posted_Date, position = NA_character_,
              location = Location, url = Link, District,
              Posting_Source = "Brockton district site (direct board)")
} else {
  brockton_df <- data.frame(title = character(0), date_posted = character(0), position = character(0),
                             location = character(0), url = character(0), District = character(0),
                             Posting_Source = character(0))
}

# Culbertson School District 17-C (Finalsite, found 2026-08-24) also
# has no structured ATS -- a plain httr2 fetch, no chromote needed, same
# pattern as the other heuristic districts above.
culbertson_districts <- registry[registry$Platform == "CulbertsonHeuristic", ]
culbertson_results <- lapply(seq_len(nrow(culbertson_districts)), function(i) {
  row <- culbertson_districts[i, ]
  df <- safe_scrape(
    row$District,
    scrape_fn = function() fetch_culbertson_postings(row$Job_Link),
    expected_cols = c("Title", "Location", "Posted_Date", "Link")
  )
  if (nrow(df) > 0) df$District <- row$District
  df
})
culbertson_df <- bind_rows(culbertson_results)
if (nrow(culbertson_df) > 0) {
  culbertson_df <- culbertson_df %>%
    transmute(title = Title, date_posted = Posted_Date, position = NA_character_,
              location = Location, url = Link, District,
              Posting_Source = "Culbertson district site (direct board)")
} else {
  culbertson_df <- data.frame(title = character(0), date_posted = character(0), position = character(0),
                               location = character(0), url = character(0), District = character(0),
                               Posting_Source = character(0))
}

# Cottonwood School District #57 (a publicly published Google Sites
# page, found 2026-08-24) also has no structured ATS -- a plain httr2
# fetch, no chromote needed, same pattern as the other heuristic
# districts above.
cottonwood57_districts <- registry[registry$Platform == "Cottonwood57Heuristic", ]
cottonwood57_results <- lapply(seq_len(nrow(cottonwood57_districts)), function(i) {
  row <- cottonwood57_districts[i, ]
  df <- safe_scrape(
    row$District,
    scrape_fn = function() fetch_cottonwood57_postings(row$Job_Link),
    expected_cols = c("Title", "Location", "Posted_Date", "Link")
  )
  if (nrow(df) > 0) df$District <- row$District
  df
})
cottonwood57_df <- bind_rows(cottonwood57_results)
if (nrow(cottonwood57_df) > 0) {
  cottonwood57_df <- cottonwood57_df %>%
    transmute(title = Title, date_posted = Posted_Date, position = NA_character_,
              location = Location, url = Link, District,
              Posting_Source = "Cottonwood district site (direct board)")
} else {
  cottonwood57_df <- data.frame(title = character(0), date_posted = character(0), position = character(0),
                                 location = character(0), url = character(0), District = character(0),
                                 Posting_Source = character(0))
}

# Creston School District (real postings live in a publicly-viewable
# Google Doc, found 2026-08-25) also has no structured ATS -- a plain
# httr2 fetch, no chromote needed, same pattern as the other heuristic
# districts above.
creston_districts <- registry[registry$Platform == "CrestonHeuristic", ]
creston_results <- lapply(seq_len(nrow(creston_districts)), function(i) {
  row <- creston_districts[i, ]
  df <- safe_scrape(
    row$District,
    scrape_fn = function() fetch_creston_postings(row$Job_Link),
    expected_cols = c("Title", "Location", "Posted_Date", "Link")
  )
  if (nrow(df) > 0) df$District <- row$District
  df
})
creston_df <- bind_rows(creston_results)
if (nrow(creston_df) > 0) {
  creston_df <- creston_df %>%
    transmute(title = Title, date_posted = Posted_Date, position = NA_character_,
              location = Location, url = Link, District,
              Posting_Source = "Creston district site (direct board)")
} else {
  creston_df <- data.frame(title = character(0), date_posted = character(0), position = character(0),
                            location = character(0), url = character(0), District = character(0),
                            Posting_Source = character(0))
}

# Clinton School District #32 (an unbranded CMS, found 2026-08-25) also
# has no structured ATS -- a plain httr2 fetch, no chromote needed, same
# pattern as the other heuristic districts above.
clinton_districts <- registry[registry$Platform == "ClintonHeuristic", ]
clinton_results <- lapply(seq_len(nrow(clinton_districts)), function(i) {
  row <- clinton_districts[i, ]
  df <- safe_scrape(
    row$District,
    scrape_fn = function() fetch_clinton_postings(row$Job_Link),
    expected_cols = c("Title", "Location", "Posted_Date", "Link")
  )
  if (nrow(df) > 0) df$District <- row$District
  df
})
clinton_df <- bind_rows(clinton_results)
if (nrow(clinton_df) > 0) {
  clinton_df <- clinton_df %>%
    transmute(title = Title, date_posted = Posted_Date, position = NA_character_,
              location = Location, url = Link, District,
              Posting_Source = "Clinton district site (direct board)")
} else {
  clinton_df <- data.frame(title = character(0), date_posted = character(0), position = character(0),
                            location = character(0), url = character(0), District = character(0),
                            Posting_Source = character(0))
}

# Dixon School District #9 (a publicly published Google Sites page,
# found 2026-08-25) also has no structured ATS -- a plain httr2 fetch,
# no chromote needed, same pattern as the other heuristic districts
# above.
dixon_districts <- registry[registry$Platform == "DixonHeuristic", ]
dixon_results <- lapply(seq_len(nrow(dixon_districts)), function(i) {
  row <- dixon_districts[i, ]
  df <- safe_scrape(
    row$District,
    scrape_fn = function() fetch_dixon_postings(row$Job_Link),
    expected_cols = c("Title", "Location", "Posted_Date", "Link")
  )
  if (nrow(df) > 0) df$District <- row$District
  df
})
dixon_df <- bind_rows(dixon_results)
if (nrow(dixon_df) > 0) {
  dixon_df <- dixon_df %>%
    transmute(title = Title, date_posted = Posted_Date, position = NA_character_,
              location = Location, url = Link, District,
              Posting_Source = "Dixon district site (direct board)")
} else {
  dixon_df <- data.frame(title = character(0), date_posted = character(0), position = character(0),
                          location = character(0), url = character(0), District = character(0),
                          Posting_Source = character(0))
}

# Elysian School District #23 (a publicly published Google Sites page,
# found 2026-08-25) also has no structured ATS -- a plain httr2 fetch,
# no chromote needed, same pattern as the other heuristic districts
# above.
elysian_districts <- registry[registry$Platform == "ElysianHeuristic", ]
elysian_results <- lapply(seq_len(nrow(elysian_districts)), function(i) {
  row <- elysian_districts[i, ]
  df <- safe_scrape(
    row$District,
    scrape_fn = function() fetch_elysian_postings(row$Job_Link),
    expected_cols = c("Title", "Location", "Posted_Date", "Link")
  )
  if (nrow(df) > 0) df$District <- row$District
  df
})
elysian_df <- bind_rows(elysian_results)
if (nrow(elysian_df) > 0) {
  elysian_df <- elysian_df %>%
    transmute(title = Title, date_posted = Posted_Date, position = NA_character_,
              location = Location, url = Link, District,
              Posting_Source = "Elysian district site (direct board)")
} else {
  elysian_df <- data.frame(title = character(0), date_posted = character(0), position = character(0),
                            location = character(0), url = character(0), District = character(0),
                            Posting_Source = character(0))
}

# Fair-Mont-Egan Schools (a publicly published Google Sites page,
# found 2026-08-25) also has no structured ATS -- a plain httr2 fetch,
# no chromote needed, same pattern as the other heuristic districts
# above.
fairmontegan_districts <- registry[registry$Platform == "FairMontEganHeuristic", ]
fairmontegan_results <- lapply(seq_len(nrow(fairmontegan_districts)), function(i) {
  row <- fairmontegan_districts[i, ]
  df <- safe_scrape(
    row$District,
    scrape_fn = function() fetch_fairmontegan_postings(row$Job_Link),
    expected_cols = c("Title", "Location", "Posted_Date", "Link")
  )
  if (nrow(df) > 0) df$District <- row$District
  df
})
fairmontegan_df <- bind_rows(fairmontegan_results)
if (nrow(fairmontegan_df) > 0) {
  fairmontegan_df <- fairmontegan_df %>%
    transmute(title = Title, date_posted = Posted_Date, position = NA_character_,
              location = Location, url = Link, District,
              Posting_Source = "Fair-Mont-Egan district site (direct board)")
} else {
  fairmontegan_df <- data.frame(title = character(0), date_posted = character(0), position = character(0),
                                 location = character(0), url = character(0), District = character(0),
                                 Posting_Source = character(0))
}

# Lustre District 23 (a publicly published Google Sites page, found
# 2026-08-25) also has no structured ATS -- a plain httr2 fetch, no
# chromote needed, same pattern as the other heuristic districts above.
lustre_districts <- registry[registry$Platform == "LustreHeuristic", ]
lustre_results <- lapply(seq_len(nrow(lustre_districts)), function(i) {
  row <- lustre_districts[i, ]
  df <- safe_scrape(
    row$District,
    scrape_fn = function() fetch_lustre_postings(row$Job_Link),
    expected_cols = c("Title", "Location", "Posted_Date", "Link")
  )
  if (nrow(df) > 0) df$District <- row$District
  df
})
lustre_df <- bind_rows(lustre_results)
if (nrow(lustre_df) > 0) {
  lustre_df <- lustre_df %>%
    transmute(title = Title, date_posted = Posted_Date, position = NA_character_,
              location = Location, url = Link, District,
              Posting_Source = "Lustre district site (direct board)")
} else {
  lustre_df <- data.frame(title = character(0), date_posted = character(0), position = character(0),
                           location = character(0), url = character(0), District = character(0),
                           Posting_Source = character(0))
}

# Miami Elementary School District #31 (a Hutterite colony school,
# found 2026-08-25) also has no structured ATS -- a plain httr2 fetch,
# no chromote needed, same pattern as the other heuristic districts
# above.
miami_districts <- registry[registry$Platform == "MiamiHeuristic", ]
miami_results <- lapply(seq_len(nrow(miami_districts)), function(i) {
  row <- miami_districts[i, ]
  df <- safe_scrape(
    row$District,
    scrape_fn = function() fetch_miami_postings(row$Job_Link),
    expected_cols = c("Title", "Location", "Posted_Date", "Link")
  )
  if (nrow(df) > 0) df$District <- row$District
  df
})
miami_df <- bind_rows(miami_results)
if (nrow(miami_df) > 0) {
  miami_df <- miami_df %>%
    transmute(title = Title, date_posted = Posted_Date, position = NA_character_,
              location = Location, url = Link, District,
              Posting_Source = "Miami district site (direct board)")
} else {
  miami_df <- data.frame(title = character(0), date_posted = character(0), position = character(0),
                          location = character(0), url = character(0), District = character(0),
                          Posting_Source = character(0))
}

# Zurich Elementary School District #17 (a Wix site, found 2026-08-25)
# also has no structured ATS -- a plain httr2 fetch, no chromote needed,
# same pattern as the other heuristic districts above.
zurich_districts <- registry[registry$Platform == "ZurichHeuristic", ]
zurich_results <- lapply(seq_len(nrow(zurich_districts)), function(i) {
  row <- zurich_districts[i, ]
  df <- safe_scrape(
    row$District,
    scrape_fn = function() fetch_zurich_postings(row$Job_Link),
    expected_cols = c("Title", "Location", "Posted_Date", "Link")
  )
  if (nrow(df) > 0) df$District <- row$District
  df
})
zurich_df <- bind_rows(zurich_results)
if (nrow(zurich_df) > 0) {
  zurich_df <- zurich_df %>%
    transmute(title = Title, date_posted = Posted_Date, position = NA_character_,
              location = Location, url = Link, District,
              Posting_Source = "Zurich district site (direct board)")
} else {
  zurich_df <- data.frame(title = character(0), date_posted = character(0), position = character(0),
                           location = character(0), url = character(0), District = character(0),
                           Posting_Source = character(0))
}

# Dayton Elementary School / Upper West Shore School District #33
# (found 2026-08-25) also has no structured ATS -- a plain httr2 fetch,
# no chromote needed, same pattern as the other heuristic districts
# above.
dayton_districts <- registry[registry$Platform == "DaytonHeuristic", ]
dayton_results <- lapply(seq_len(nrow(dayton_districts)), function(i) {
  row <- dayton_districts[i, ]
  df <- safe_scrape(
    row$District,
    scrape_fn = function() fetch_dayton_postings(row$Job_Link),
    expected_cols = c("Title", "Location", "Posted_Date", "Link")
  )
  if (nrow(df) > 0) df$District <- row$District
  df
})
dayton_df <- bind_rows(dayton_results)
if (nrow(dayton_df) > 0) {
  dayton_df <- dayton_df %>%
    transmute(title = Title, date_posted = Posted_Date, position = NA_character_,
              location = Location, url = Link, District,
              Posting_Source = "Dayton district site (direct board)")
} else {
  dayton_df <- data.frame(title = character(0), date_posted = character(0), position = character(0),
                           location = character(0), url = character(0), District = character(0),
                           Posting_Source = character(0))
}

# Lincoln School District #38 (a publicly published Google Sites page,
# found 2026-08-24) also has no structured ATS -- a plain httr2 fetch,
# no chromote needed, same pattern as the other heuristic districts
# above.
lincoln_districts <- registry[registry$Platform == "LincolnHeuristic", ]
lincoln_results <- lapply(seq_len(nrow(lincoln_districts)), function(i) {
  row <- lincoln_districts[i, ]
  df <- safe_scrape(
    row$District,
    scrape_fn = function() fetch_lincoln_postings(row$Job_Link),
    expected_cols = c("Title", "Location", "Posted_Date", "Link")
  )
  if (nrow(df) > 0) df$District <- row$District
  df
})
lincoln_df <- bind_rows(lincoln_results)
if (nrow(lincoln_df) > 0) {
  lincoln_df <- lincoln_df %>%
    transmute(title = Title, date_posted = Posted_Date, position = NA_character_,
              location = Location, url = Link, District,
              Posting_Source = "Lincoln district site (direct board)")
} else {
  lincoln_df <- data.frame(title = character(0), date_posted = character(0), position = character(0),
                            location = character(0), url = character(0), District = character(0),
                            Posting_Source = character(0))
}

# Independent School (a publicly published Google Sites page, found
# 2026-08-24) also has no structured ATS -- a plain httr2 fetch, no
# chromote needed, same pattern as the other heuristic districts above.
independent_districts <- registry[registry$Platform == "IndependentHeuristic", ]
independent_results <- lapply(seq_len(nrow(independent_districts)), function(i) {
  row <- independent_districts[i, ]
  df <- safe_scrape(
    row$District,
    scrape_fn = function() fetch_independent_postings(row$Job_Link),
    expected_cols = c("Title", "Location", "Posted_Date", "Link")
  )
  if (nrow(df) > 0) df$District <- row$District
  df
})
independent_df <- bind_rows(independent_results)
if (nrow(independent_df) > 0) {
  independent_df <- independent_df %>%
    transmute(title = Title, date_posted = Posted_Date, position = NA_character_,
              location = Location, url = Link, District,
              Posting_Source = "Independent district site (direct board)")
} else {
  independent_df <- data.frame(title = character(0), date_posted = character(0), position = character(0),
                                location = character(0), url = character(0), District = character(0),
                                Posting_Source = character(0))
}

# Shepherd School District #37 (Finalsite, found 2026-08-24) also has no
# structured ATS in this project's own platform list -- a plain httr2
# fetch, no chromote needed, same pattern as Thompson Falls/Hobson
# above.
shepherd_districts <- registry[registry$Platform == "ShepherdHeuristic", ]
shepherd_results <- lapply(seq_len(nrow(shepherd_districts)), function(i) {
  row <- shepherd_districts[i, ]
  df <- safe_scrape(
    row$District,
    scrape_fn = function() fetch_shepherd_postings(row$Job_Link),
    expected_cols = c("Title", "Location", "Posted_Date", "Link")
  )
  if (nrow(df) > 0) df$District <- row$District
  df
})
shepherd_df <- bind_rows(shepherd_results)
if (nrow(shepherd_df) > 0) {
  shepherd_df <- shepherd_df %>%
    transmute(title = Title, date_posted = Posted_Date, position = NA_character_,
              location = Location, url = Link, District,
              Posting_Source = "Shepherd district site (direct board)")
} else {
  shepherd_df <- data.frame(title = character(0), date_posted = character(0), position = character(0),
                             location = character(0), url = character(0), District = character(0),
                             Posting_Source = character(0))
}

# Hysham Public Schools (unbranded CMS, found 2026-08-24) also has no
# structured ATS in this project's own platform list -- a plain httr2
# fetch, no chromote needed, same pattern as the other heuristic
# districts above.
hysham_districts <- registry[registry$Platform == "HyshamHeuristic", ]
hysham_results <- lapply(seq_len(nrow(hysham_districts)), function(i) {
  row <- hysham_districts[i, ]
  df <- safe_scrape(
    row$District,
    scrape_fn = function() fetch_hysham_postings(row$Job_Link),
    expected_cols = c("Title", "Location", "Posted_Date", "Link")
  )
  if (nrow(df) > 0) df$District <- row$District
  df
})
hysham_df <- bind_rows(hysham_results)
if (nrow(hysham_df) > 0) {
  hysham_df <- hysham_df %>%
    transmute(title = Title, date_posted = Posted_Date, position = NA_character_,
              location = Location, url = Link, District,
              Posting_Source = "Hysham district site (direct board)")
} else {
  hysham_df <- data.frame(title = character(0), date_posted = character(0), position = character(0),
                           location = character(0), url = character(0), District = character(0),
                           Posting_Source = character(0))
}

# Swan River School District #4 (WordPress, found 2026-08-24) also has
# no structured ATS in this project's own platform list -- a plain httr2
# fetch, no chromote needed, same pattern as the other heuristic
# districts above.
swanriver_districts <- registry[registry$Platform == "SwanRiverHeuristic", ]
swanriver_results <- lapply(seq_len(nrow(swanriver_districts)), function(i) {
  row <- swanriver_districts[i, ]
  df <- safe_scrape(
    row$District,
    scrape_fn = function() fetch_swanriver_postings(row$Job_Link),
    expected_cols = c("Title", "Location", "Posted_Date", "Link")
  )
  if (nrow(df) > 0) df$District <- row$District
  df
})
swanriver_df <- bind_rows(swanriver_results)
if (nrow(swanriver_df) > 0) {
  swanriver_df <- swanriver_df %>%
    transmute(title = Title, date_posted = Posted_Date, position = NA_character_,
              location = Location, url = Link, District,
              Posting_Source = "Swan River district site (direct board)")
} else {
  swanriver_df <- data.frame(title = character(0), date_posted = character(0), position = character(0),
                              location = character(0), url = character(0), District = character(0),
                              Posting_Source = character(0))
}

# Bigfork School District 38 (WordPress, found 2026-08-24) also has no
# structured ATS in this project's own platform list -- a plain httr2
# fetch, no chromote needed, same pattern as the other heuristic
# districts above.
bigfork_districts <- registry[registry$Platform == "BigforkHeuristic", ]
bigfork_results <- lapply(seq_len(nrow(bigfork_districts)), function(i) {
  row <- bigfork_districts[i, ]
  df <- safe_scrape(
    row$District,
    scrape_fn = function() fetch_bigfork_postings(row$Job_Link),
    expected_cols = c("Title", "Location", "Posted_Date", "Link")
  )
  if (nrow(df) > 0) df$District <- row$District
  df
})
bigfork_df <- bind_rows(bigfork_results)
if (nrow(bigfork_df) > 0) {
  bigfork_df <- bigfork_df %>%
    transmute(title = Title, date_posted = Posted_Date, position = NA_character_,
              location = Location, url = Link, District,
              Posting_Source = "Bigfork district site (direct board)")
} else {
  bigfork_df <- data.frame(title = character(0), date_posted = character(0), position = character(0),
                            location = character(0), url = character(0), District = character(0),
                            Posting_Source = character(0))
}

# Reed Point School District (a publicly published Google Sites page,
# found 2026-08-24) also has no structured ATS -- a plain httr2 fetch,
# no chromote needed, same pattern as Custer/Scobey/Ramsay/Roy/Arrowhead/
# North Star/Shields Valley/Thompson Falls/Ekalaka/Trego above.
reedpoint_districts <- registry[registry$Platform == "ReedPointHeuristic", ]
reedpoint_results <- lapply(seq_len(nrow(reedpoint_districts)), function(i) {
  row <- reedpoint_districts[i, ]
  df <- safe_scrape(
    row$District,
    scrape_fn = function() fetch_reedpoint_postings(row$Job_Link),
    expected_cols = c("Title", "Location", "Posted_Date", "Link")
  )
  if (nrow(df) > 0) df$District <- row$District
  df
})
reedpoint_df <- bind_rows(reedpoint_results)
if (nrow(reedpoint_df) > 0) {
  reedpoint_df <- reedpoint_df %>%
    transmute(title = Title, date_posted = Posted_Date, position = NA_character_,
              location = Location, url = Link, District,
              Posting_Source = "Reed Point district site (direct board)")
} else {
  reedpoint_df <- data.frame(title = character(0), date_posted = character(0), position = character(0),
                              location = character(0), url = character(0), District = character(0),
                              Posting_Source = character(0))
}

# Hobson Public School (Finalsite, found 2026-08-24) also has no
# structured ATS in this project's own platform list -- a plain httr2
# fetch, no chromote needed, same pattern as Thompson Falls above.
hobson_districts <- registry[registry$Platform == "HobsonHeuristic", ]
hobson_results <- lapply(seq_len(nrow(hobson_districts)), function(i) {
  row <- hobson_districts[i, ]
  df <- safe_scrape(
    row$District,
    scrape_fn = function() fetch_hobson_postings(row$Job_Link),
    expected_cols = c("Title", "Location", "Posted_Date", "Link")
  )
  if (nrow(df) > 0) df$District <- row$District
  df
})
hobson_df <- bind_rows(hobson_results)
if (nrow(hobson_df) > 0) {
  hobson_df <- hobson_df %>%
    transmute(title = Title, date_posted = Posted_Date, position = NA_character_,
              location = Location, url = Link, District,
              Posting_Source = "Hobson district site (direct board)")
} else {
  hobson_df <- data.frame(title = character(0), date_posted = character(0), position = character(0),
                           location = character(0), url = character(0), District = character(0),
                           Posting_Source = character(0))
}

# Turner Public Schools (WordPress, found 2026-08-24) also has no
# structured ATS in this project's own platform list -- a plain httr2
# fetch, no chromote needed, same pattern as Ramsay above.
turner_districts <- registry[registry$Platform == "TurnerHeuristic", ]
turner_results <- lapply(seq_len(nrow(turner_districts)), function(i) {
  row <- turner_districts[i, ]
  df <- safe_scrape(
    row$District,
    scrape_fn = function() fetch_turner_postings(row$Job_Link),
    expected_cols = c("Title", "Location", "Posted_Date", "Link")
  )
  if (nrow(df) > 0) df$District <- row$District
  df
})
turner_df <- bind_rows(turner_results)
if (nrow(turner_df) > 0) {
  turner_df <- turner_df %>%
    transmute(title = Title, date_posted = Posted_Date, position = NA_character_,
              location = Location, url = Link, District,
              Posting_Source = "Turner district site (direct board)")
} else {
  turner_df <- data.frame(title = character(0), date_posted = character(0), position = character(0),
                           location = character(0), url = character(0), District = character(0),
                           Posting_Source = character(0))
}

# Terry Public Schools (Squarespace, found 2026-08-24) also has no
# structured ATS in this project's own platform list -- a plain httr2
# fetch, no chromote needed, same pattern as the other heuristic
# districts above.
terry_districts <- registry[registry$Platform == "TerryHeuristic", ]
terry_results <- lapply(seq_len(nrow(terry_districts)), function(i) {
  row <- terry_districts[i, ]
  df <- safe_scrape(
    row$District,
    scrape_fn = function() fetch_terry_postings(row$Job_Link),
    expected_cols = c("Title", "Location", "Posted_Date", "Link")
  )
  if (nrow(df) > 0) df$District <- row$District
  df
})
terry_df <- bind_rows(terry_results)
if (nrow(terry_df) > 0) {
  terry_df <- terry_df %>%
    transmute(title = Title, date_posted = Posted_Date, position = NA_character_,
              location = Location, url = Link, District,
              Posting_Source = "Terry district site (direct board)")
} else {
  terry_df <- data.frame(title = character(0), date_posted = character(0), position = character(0),
                          location = character(0), url = character(0), District = character(0),
                          Posting_Source = character(0))
}

# Gallatin Gateway School (CatapultCMS, found 2026-08-24) also has no
# structured ATS in this project's own platform list -- a plain httr2
# fetch, no chromote needed, same pattern as the other heuristic
# districts above.
gallatingateway_districts <- registry[registry$Platform == "GallatinGatewayHeuristic", ]
gallatingateway_results <- lapply(seq_len(nrow(gallatingateway_districts)), function(i) {
  row <- gallatingateway_districts[i, ]
  df <- safe_scrape(
    row$District,
    scrape_fn = function() fetch_gallatingateway_postings(row$Job_Link),
    expected_cols = c("Title", "Location", "Posted_Date", "Link")
  )
  if (nrow(df) > 0) df$District <- row$District
  df
})
gallatingateway_df <- bind_rows(gallatingateway_results)
if (nrow(gallatingateway_df) > 0) {
  gallatingateway_df <- gallatingateway_df %>%
    transmute(title = Title, date_posted = Posted_Date, position = NA_character_,
              location = Location, url = Link, District,
              Posting_Source = "Gallatin Gateway district site (direct board)")
} else {
  gallatingateway_df <- data.frame(title = character(0), date_posted = character(0), position = character(0),
                                    location = character(0), url = character(0), District = character(0),
                                    Posting_Source = character(0))
}

# The browser-backed districts use a shared Chromote session because their
# Apptegy/CyberSchool pages require JavaScript to render (a plain httr2
# request receives a bot-challenge shell). Each district is independently
# wrapped by fetch_apptegy_k12_postings(), so a changed page is logged without
# discarding healthy districts' results. The outer safe_scrape() protects the
# pipeline if the shared session itself cannot start.
apptegy_raw <- safe_scrape(
  "Apptegy/chromote K-12 districts (Wolf Point, Plentywood, Conrad, Westby, Choteau, Gardiner, Malta, Drummond, Deer Lodge, Townsend, Hays-Lodge Pole, Plevna, Sunburst, Belt, Big Sky, Melstone, Roundup, White Sulphur Springs, Shelby, Centerville, Geyser, Arlee, Chinook, Darby, Dutton/Brady, St. Ignatius, Stanford, Lolo, Froid, Huntley Project, Park City, Alberton, Dillon, Ennis, Columbus, St Regis, Florence-Carlton, West Yellowstone, Bonner, Deer Park, Evergreen, Lone Rock)",
  scrape_fn = function() fetch_apptegy_k12_postings(chromote_session_factory = function() ChromoteSession$new()),
  expected_cols = c("Title", "Location", "Posted_Date", "Link", "District")
)
if (nrow(apptegy_raw) > 0) {
  apptegy_df <- apptegy_raw %>%
    transmute(title = Title, date_posted = Posted_Date, position = NA_character_,
              location = Location, url = Link, District,
              Posting_Source = "Apptegy district site (direct board)")
} else {
  apptegy_df <- data.frame(title = character(0), date_posted = character(0), position = character(0),
                            location = character(0), url = character(0), District = character(0),
                            Posting_Source = character(0))
}
```

### OPI "Jobs for Teachers" statewide fallback feed
```{r k12 opi statewide feed, message=FALSE, warning=FALSE, echo=TRUE}
library(dplyr)
source("scrape_helpers.R")
source("direct_api_scrapers.R")

# Montana's analog of Wyoming's WSBA vacancies page. OPI is a statewide
# supplementary source, including direct-scraper cities, but its publication
# rules and completeness have not been independently established. It stays
# intact here; exact posting-level overlaps with direct boards are removed
# only after every source's date fields have been standardized below. This
# avoids losing independent employers that happen to share a city with a
# covered district.
opi_raw <- safe_scrape(
  "OPI Jobs for Teachers (statewide)",
  scrape_fn = fetch_opi_statewide_postings,
  expected_cols = c("Title", "Location", "Posted_Date", "Link")
)

opi_df <- opi_raw
if (nrow(opi_df) > 0) {
  # District is NOT a canonical legal district name here -- OPI's feed only
  # exposes a City column, so District is that raw City value passed
  # through, the closest available proxy (same honesty tradeoff as every
  # other source's raw `location` field, just one level up). Flagged in
  # DATA_COOKBOOK.md once that's written.
  opi_df <- opi_df %>%
    transmute(title = Title, date_posted = Posted_Date, position = NA_character_,
              location = Location, url = Link, District = Location,
              Posting_Source = "OPI Jobs for Teachers (statewide)")
} else {
  opi_df <- data.frame(title = character(0), date_posted = character(0), position = character(0),
                        location = character(0), url = character(0), District = character(0),
                        Posting_Source = character(0))
}
```

### Combine all K-12 data, classify, archive, and accumulate history
```{r combine k12 data, echo=TRUE, warning=FALSE, message=FALSE}
library(stringr)
library(dplyr)
library(lubridate)

standardize_date <- function(x) {
  x <- as.character(x)
  x <- str_remove(x, "\\s*\\(.*\\)$")
  parsed <- parse_date_time(
    x,
    orders = c("b d Y h:M p", "B d Y h:M p", "ymd", "mdy", "dmy", "Y-m-d H:M:S"),
    tz = "UTC", quiet = TRUE
  )
  as.Date(parsed)
}

applitrack_df <- applitrack_df %>% mutate(date_posted = standardize_date(date_posted))
schoolspring_df <- schoolspring_df %>% mutate(date_posted = standardize_date(date_posted))
tylerportico_df <- tylerportico_df %>% mutate(date_posted = standardize_date(date_posted))
tedk12_df <- tedk12_df %>% mutate(date_posted = standardize_date(date_posted))
livingston_df <- livingston_df %>% mutate(date_posted = standardize_date(date_posted))
lodgegrass_df <- lodgegrass_df %>% mutate(date_posted = standardize_date(date_posted))
broadview_df <- broadview_df %>% mutate(date_posted = standardize_date(date_posted))
custer_df <- custer_df %>% mutate(date_posted = standardize_date(date_posted))
scobey_df <- scobey_df %>% mutate(date_posted = standardize_date(date_posted))
ramsay_df <- ramsay_df %>% mutate(date_posted = standardize_date(date_posted))
roy_df <- roy_df %>% mutate(date_posted = standardize_date(date_posted))
arrowhead_df <- arrowhead_df %>% mutate(date_posted = standardize_date(date_posted))
northstar_df <- northstar_df %>% mutate(date_posted = standardize_date(date_posted))
shieldsvalley_df <- shieldsvalley_df %>% mutate(date_posted = standardize_date(date_posted))
thompsonfalls_df <- thompsonfalls_df %>% mutate(date_posted = standardize_date(date_posted))
ekalaka_df <- ekalaka_df %>% mutate(date_posted = standardize_date(date_posted))
trego_df <- trego_df %>% mutate(date_posted = standardize_date(date_posted))
reedpoint_df <- reedpoint_df %>% mutate(date_posted = standardize_date(date_posted))
hobson_df <- hobson_df %>% mutate(date_posted = standardize_date(date_posted))
turner_df <- turner_df %>% mutate(date_posted = standardize_date(date_posted))
terry_df <- terry_df %>% mutate(date_posted = standardize_date(date_posted))
gallatingateway_df <- gallatingateway_df %>% mutate(date_posted = standardize_date(date_posted))
swanriver_df <- swanriver_df %>% mutate(date_posted = standardize_date(date_posted))
bigfork_df <- bigfork_df %>% mutate(date_posted = standardize_date(date_posted))
lincoln_df <- lincoln_df %>% mutate(date_posted = standardize_date(date_posted))
independent_df <- independent_df %>% mutate(date_posted = standardize_date(date_posted))
shepherd_df <- shepherd_df %>% mutate(date_posted = standardize_date(date_posted))
hysham_df <- hysham_df %>% mutate(date_posted = standardize_date(date_posted))
baker_df <- baker_df %>% mutate(date_posted = standardize_date(date_posted))
cutbank_df <- cutbank_df %>% mutate(date_posted = standardize_date(date_posted))
hinsdale_df <- hinsdale_df %>% mutate(date_posted = standardize_date(date_posted))
valier_df <- valier_df %>% mutate(date_posted = standardize_date(date_posted))
roberts_df <- roberts_df %>% mutate(date_posted = standardize_date(date_posted))
winnett_df <- winnett_df %>% mutate(date_posted = standardize_date(date_posted))
milescity_df <- milescity_df %>% mutate(date_posted = standardize_date(date_posted))
augusta_df <- augusta_df %>% mutate(date_posted = standardize_date(date_posted))
brockton_df <- brockton_df %>% mutate(date_posted = standardize_date(date_posted))
culbertson_df <- culbertson_df %>% mutate(date_posted = standardize_date(date_posted))
cottonwood57_df <- cottonwood57_df %>% mutate(date_posted = standardize_date(date_posted))
creston_df <- creston_df %>% mutate(date_posted = standardize_date(date_posted))
clinton_df <- clinton_df %>% mutate(date_posted = standardize_date(date_posted))
dixon_df <- dixon_df %>% mutate(date_posted = standardize_date(date_posted))
elysian_df <- elysian_df %>% mutate(date_posted = standardize_date(date_posted))
fairmontegan_df <- fairmontegan_df %>% mutate(date_posted = standardize_date(date_posted))
lustre_df <- lustre_df %>% mutate(date_posted = standardize_date(date_posted))
miami_df <- miami_df %>% mutate(date_posted = standardize_date(date_posted))
zurich_df <- zurich_df %>% mutate(date_posted = standardize_date(date_posted))
dayton_df <- dayton_df %>% mutate(date_posted = standardize_date(date_posted))
apptegy_df <- apptegy_df %>% mutate(date_posted = standardize_date(date_posted))
opi_df <- opi_df %>% mutate(date_posted = standardize_date(date_posted))

direct_df <- bind_rows(applitrack_df, schoolspring_df, tylerportico_df, tedk12_df,
                       livingston_df, lodgegrass_df, broadview_df, custer_df, scobey_df, ramsay_df,
                       roy_df, arrowhead_df, northstar_df, shieldsvalley_df, thompsonfalls_df, ekalaka_df, trego_df,
                       lincoln_df, independent_df, shepherd_df, hysham_df, baker_df, cutbank_df, hinsdale_df, valier_df,
                       roberts_df, winnett_df, milescity_df, augusta_df, brockton_df, culbertson_df, cottonwood57_df,
                       creston_df, clinton_df, dixon_df, elysian_df, fairmontegan_df, lustre_df, miami_df, zurich_df, dayton_df,
                       swanriver_df, bigfork_df, reedpoint_df, hobson_df, turner_df, terry_df,
                       gallatingateway_df, apptegy_df)
opi_df <- remove_opi_direct_duplicates(opi_df, direct_df, registry)

combined <- bind_rows(direct_df, opi_df) %>%
  mutate(
    across(c(title, position, location, url, District, Posting_Source), normalize_posting_text),
    Archive_Date = Sys.Date()
  ) %>%
  add_k12_posting_identity() %>%
  distinct(Posting_ID, .keep_all = TRUE)

if (!dir.exists("Archivek12_Data")) dir.create("Archivek12_Data")
file_name <- paste0("combined_", Sys.Date(), ".csv")
write.csv(combined, file = file.path("Archivek12_Data", file_name), row.names = FALSE)

combinedclean <- combined %>%
  mutate(position = classify_k12_position(title),
         District = canonicalize_k12_district(District)) %>%
  select(title, Archive_Date, date_posted, position, location, url, District,
         Posting_Source, Posting_Identity_Method, Posting_ID)

if (!dir.exists("Mt_Ed_Jobs")) dir.create("Mt_Ed_Jobs")
write.csv(combinedclean, file = file.path("Mt_Ed_Jobs", "combinedclean.csv"), row.names = FALSE)

source("history_accumulator.R")

this_week_k12jobs <- combinedclean %>%
  filter(position == "Teacher") %>%
  mutate(Category = classify_k12_subject(title),
         Broad_Category = classify_k12_broad_category(Category)) %>%
  select(title, Archive_Date, position, location, url, District,
         Posting_Source, Posting_Identity_Method, Posting_ID, Category, Broad_Category)

k12jobs <- append_weekly_rows(file.path("Mt_Ed_Jobs", "k12jobanalysis.csv"), this_week_k12jobs)
write.csv(k12jobs, file = file.path("Mt_Ed_Jobs", "k12jobanalysis.csv"), row.names = FALSE)

this_week_district_totals <- combinedclean %>%
  group_by(District, Archive_Date) %>%
  summarize(n = n_distinct(Posting_ID), .groups = "drop")
k12_district_weekly_totals <- append_weekly_rows(
  file.path("Mt_Ed_Jobs", "k12_district_weekly_totals.csv"), this_week_district_totals)
write.csv(k12_district_weekly_totals, file.path("Mt_Ed_Jobs", "k12_district_weekly_totals.csv"), row.names = FALSE)

# Every current and historical K-12 count uses the posting identity contract:
# stable per-posting URLs where a source provides one, otherwise the explicit
# source/OPI fallback documented in DATA_COOKBOOK.md.
this_week_k12sumdistrict <- summarize_k12_posting_counts(this_week_k12jobs)

this_week_k12sum <- this_week_k12sumdistrict %>%
  group_by(Broad_Category, Archive_Date) %>%
  summarize(sum = sum(sum), .groups = "drop") %>%
  mutate(District = "Total") %>%
  select(Broad_Category, Archive_Date, District, sum)

check_total_matches_parts(this_week_k12sum, this_week_k12sumdistrict,
                           group_cols = c("Broad_Category", "Archive_Date"))

this_week_allsum <- bind_rows(this_week_k12sum, this_week_k12sumdistrict)
Allsum <- append_weekly_rows(file.path("Mt_Ed_Jobs", "allsum.csv"), this_week_allsum)
write.csv(Allsum, file = file.path("Mt_Ed_Jobs", "allsum.csv"), row.names = FALSE)

k12districtnowsum <- this_week_k12sumdistrict %>%
  ungroup() %>%
  rename(Sum = sum) %>%
  select(Broad_Category, Sum, District)

k12nowsum <- k12districtnowsum %>%
  group_by(Broad_Category) %>%
  summarize(Sum = sum(Sum), .groups = "drop") %>%
  mutate(District = "Total")

Allnow <- bind_rows(k12nowsum, k12districtnowsum)
write.csv(Allnow, file = file.path("Mt_Ed_Jobs", "allnow.csv"), row.names = FALSE)
```

### K-12 teacher salary (MT DLI Teacher Compensation Report) and staffing (CCD teacher FTE via Urban Institute)
```{r k12 salary and staffing data, message=FALSE, warning=FALSE, echo=TRUE}
library(dplyr)
source("scrape_helpers.R")
source("salary_scrapers.R")
source("ccd_staff_scraper.R")

teacher_salary <- safe_scrape(
  "MT DLI teacher compensation",
  scrape_fn = fetch_dli_teacher_compensation_all_districts,
  expected_cols = c("District", "Teacher_Count", "Teacher_Salary_10th_Pctile",
                     "Teacher_Avg_Salary", "Teacher_Salary_90th_Pctile", "Salary_Year")
)

teacher_fte <- safe_scrape(
  "CCD district teacher FTE (MT)",
  scrape_fn = fetch_ccd_teacher_fte,
  expected_cols = c("District", "Teachers_Total_FTE", "Enrollment", "CCD_Year")
)

# Static geo/link fields (County, Latitude, Longitude, Job_Link) come from
# the district registry -- salarymap2.csv doesn't exist as its own separate
# hand-maintained file the way Wyoming's does (this project's registry
# already carries the same hand-maintained columns). A failed fetch leaves
# last run's good salary/staffing values untouched rather than blanking
# them out, same "leave it alone, don't blank it out" behavior every other
# salary/staffing chunk in this pipeline has (see Wyoming's equivalent
# chunks) -- so salarymap2.csv is read back first (if it exists) rather
# than rebuilt fresh from the registry every run.
registry <- read.csv("k12_district_registry.csv", stringsAsFactors = FALSE) %>%
  select(District, County, Latitude, Longitude, Job_Link)

salarymap2_path <- file.path("Mt_Ed_Jobs", "salarymap2.csv")
salarymap2 <- if (file.exists(salarymap2_path)) {
  read.csv(salarymap2_path, fileEncoding = "UTF-8") %>%
    select(-any_of(c("County", "Latitude", "Longitude", "Job_Link"))) %>%
    right_join(registry, by = "District") %>%
    select(District, County, Latitude, Longitude, Job_Link, everything())
} else {
  registry
}

if (nrow(teacher_salary) > 0) {
  salarymap2 <- salarymap2 %>%
    select(-any_of(c("Teacher_Count", "Teacher_Salary_10th_Pctile", "Teacher_Avg_Salary",
                      "Teacher_Salary_90th_Pctile", "Salary_Year", "Salary_Source"))) %>%
    left_join(teacher_salary, by = "District") %>%
    mutate(Salary_Source = "MT Dept. of Labor & Industry Teacher Compensation Report (lmi.mt.gov/publications)")

  # Starts building a multi-year K-12 salary trend -- MT DLI has no public
  # historical archive (only the current edition's PDFs are ever
  # published, confirmed live). Complete snapshots are idempotent while a
  # partial prior district/year set is safely backfilled.
  archive_k12_salary_snapshot(salarymap2, file.path("Mt_Ed_Jobs", "k12_salary_history.csv"))
} else {
  message("MT DLI teacher compensation fetch failed -- leaving salarymap2.csv's salary columns untouched this run.")
}

if (nrow(teacher_fte) > 0) {
  salarymap2 <- salarymap2 %>%
    select(-any_of(c("Teachers_Total_FTE", "Enrollment", "CCD_Year", "CCD_Source"))) %>%
    left_join(teacher_fte, by = "District") %>%
    mutate(CCD_Source = "NCES Common Core of Data via Urban Institute Education Data Portal (educationdata.urban.org)")
} else {
  message("CCD teacher FTE fetch failed -- leaving salarymap2.csv's staffing columns untouched this run.")
}

write.csv(salarymap2, salarymap2_path, row.names = FALSE)
```

### K-12 county-level context (income, rent, mining/energy employment share, population trend) and district-level child poverty rate, from the Census Bureau
```{r k12 census county and district context, message=FALSE, warning=FALSE, echo=TRUE}
library(dplyr)
source("scrape_helpers.R")
source("census_acs_scraper.R")
source("census_saipe_scraper.R")
source("opi_finance_scraper.R")

# CENSUS_API_KEY must be set (a GitHub Actions secret in CI, .Renviron
# locally). safe_scrape() catches a missing/invalid key the same way it
# catches any other fetch failure: logs it, leaves salarymap2.csv untouched
# this run, rather than crashing the whole pipeline.
county_context <- safe_scrape(
  "Census ACS county context (MT)",
  scrape_fn = fetch_census_county_context,
  expected_cols = c("County", "Median_Household_Income", "Median_Gross_Rent",
                     "Population", "ACS_Year", "Mining_Employment_Share", "Population_Change_Pct")
)

if (nrow(county_context) > 0) {
  salarymap2 <- read.csv(salarymap2_path, fileEncoding = "UTF-8") %>%
    select(-any_of(c("Median_Household_Income", "Median_Gross_Rent", "Population",
                      "ACS_Year", "Mining_Employment_Share", "Population_Change_Pct"))) %>%
    left_join(county_context, by = "County")
  write.csv(salarymap2, salarymap2_path, row.names = FALSE)
} else {
  message("Census ACS county context fetch failed -- leaving salarymap2.csv untouched this run.")
}

child_poverty <- safe_scrape(
  "Census SAIPE district child poverty rate (MT)",
  scrape_fn = fetch_census_saipe_child_poverty,
  expected_cols = c("District", "Child_Poverty_Rate", "SAIPE_Year")
)

if (nrow(child_poverty) > 0) {
  salarymap2 <- read.csv(salarymap2_path, fileEncoding = "UTF-8") %>%
    select(-any_of(c("Child_Poverty_Rate", "SAIPE_Year"))) %>%
    left_join(child_poverty, by = "District")
  write.csv(salarymap2, salarymap2_path, row.names = FALSE)
} else {
  message("Census SAIPE child poverty fetch failed -- leaving salarymap2.csv untouched this run.")
}

district_finance <- safe_scrape(
  "OPI per-district General Fund expenditures (MT)",
  scrape_fn = fetch_opi_district_expenditures,
  expected_cols = c("District", "Total_General_Fund_Expenditure", "Finance_FY")
)

if (nrow(district_finance) > 0) {
  salarymap2 <- read.csv(salarymap2_path, fileEncoding = "UTF-8") %>%
    select(-any_of(c("Total_General_Fund_Expenditure", "Finance_FY", "Finance_Source"))) %>%
    left_join(district_finance, by = "District") %>%
    mutate(Finance_Source = "OPI School Finance Data Files (opi.mt.gov/Leadership/Finance-Grants/School-Finance/OPI-Financial-Data-Files)")
  write.csv(salarymap2, salarymap2_path, row.names = FALSE)
} else {
  message("OPI district finance fetch failed -- leaving salarymap2.csv untouched this run.")
}
```


## Part 2: Montana Higher Ed Data

### HE institutions scraped directly (PeopleAdmin, JazzHR, Paycom, heuristic sources)
```{r he direct-platform institutions, message=FALSE, warning=FALSE, echo=TRUE}
library(dplyr)
library(chromote)
source("scrape_helpers.R")
source("direct_api_scrapers.R")
source("misc_college_scrapers.R")

he_registry <- read.csv("he_institution_registry.csv", stringsAsFactors = FALSE)

peopleadmin_institutions <- he_registry[he_registry$Platform == "PeopleAdmin", ]
peopleadmin_results <- lapply(seq_len(nrow(peopleadmin_institutions)), function(i) {
  row <- peopleadmin_institutions[i, ]
  df <- safe_scrape(
    row$Institution,
    scrape_fn = function() fetch_peopleadmin_atom(row$Feed_URL, location_fallback = row$Institution),
    expected_cols = c("Title", "Location", "Posted_Date", "Link")
  )
  if (nrow(df) > 0) df$Institution <- row$Institution
  df
})
peopleadmin_df <- bind_rows(peopleadmin_results)

# Institution is NOT overwritten from the registry row here (unlike every
# other platform below) -- parse_jazzhr_postings() already attributes each
# posting to its real institution (Montana Tech vs. Highlands College,
# 2026-08-07), and blindly reassigning row$Institution here would
# silently erase that split.
jazzhr_institutions <- he_registry[he_registry$Platform == "JazzHR", ]
jazzhr_results <- lapply(seq_len(nrow(jazzhr_institutions)), function(i) {
  row <- jazzhr_institutions[i, ]
  safe_scrape(
    row$Institution,
    scrape_fn = function() fetch_jazzhr_postings(row$Feed_URL, row$Institution),
    expected_cols = c("Title", "Location", "Posted_Date", "Link", "Institution")
  )
})
jazzhr_df <- bind_rows(jazzhr_results)

paycom_institutions <- he_registry[he_registry$Platform == "Paycom", ]
paycom_results <- lapply(seq_len(nrow(paycom_institutions)), function(i) {
  row <- paycom_institutions[i, ]
  df <- safe_scrape(
    row$Institution,
    scrape_fn = function() fetch_paycom_postings(row$Feed_URL, row$Institution),
    expected_cols = c("Title", "Location", "Posted_Date", "Link")
  )
  if (nrow(df) > 0) df$Institution <- row$Institution
  df
})
paycom_df <- bind_rows(paycom_results)

# Miles Community College has no structured ATS -- MilesCCHeuristic scrapes
# its own employment page's free-text prose directly (misc_college_scrapers.R),
# a real but acknowledged-less-reliable source, same spirit as Wyoming's
# misc_district_scrapers.R on the K-12 side.
milescc_institutions <- he_registry[he_registry$Platform == "MilesCCHeuristic", ]
milescc_results <- lapply(seq_len(nrow(milescc_institutions)), function(i) {
  row <- milescc_institutions[i, ]
  df <- safe_scrape(
    row$Institution,
    scrape_fn = function() fetch_miles_cc_postings(row$Feed_URL),
    expected_cols = c("Title", "Location", "Posted_Date", "Link")
  )
  if (nrow(df) > 0) df$Institution <- row$Institution
  df
})
milescc_df <- bind_rows(milescc_results)

# Dawson Community College also has no structured ATS -- DawsonCCHeuristic
# scrapes its employment page's labeled "Openings" sections directly
# (misc_college_scrapers.R), same heuristic-source caveat as Miles CC above.
dawsoncc_institutions <- he_registry[he_registry$Platform == "DawsonCCHeuristic", ]
dawsoncc_results <- lapply(seq_len(nrow(dawsoncc_institutions)), function(i) {
  row <- dawsoncc_institutions[i, ]
  df <- safe_scrape(
    row$Institution,
    scrape_fn = function() fetch_dawson_cc_postings(row$Feed_URL),
    expected_cols = c("Title", "Location", "Posted_Date", "Link")
  )
  if (nrow(df) > 0) df$Institution <- row$Institution
  df
})
dawsoncc_df <- bind_rows(dawsoncc_results)

# Blackfeet Community College runs isolved Hire (applican) -- Feed_URL packs
# "subdomain:domain_id" since the platform needs both to build its jobs API
# URL (https://{subdomain}.isolvedhire.com/core/jobs/{domain_id}), and
# domain_id is a per-institution site ID with no derivable relationship to
# the subdomain (only discoverable via live network capture).
isolvedhire_institutions <- he_registry[he_registry$Platform == "IsolvedHire", ]
isolvedhire_results <- lapply(seq_len(nrow(isolvedhire_institutions)), function(i) {
  row <- isolvedhire_institutions[i, ]
  feed_parts <- strsplit(row$Feed_URL, ":")[[1]]
  df <- safe_scrape(
    row$Institution,
    scrape_fn = function() fetch_isolvedhire_postings(feed_parts[1], feed_parts[2], row$Institution),
    expected_cols = c("Title", "Location", "Posted_Date", "Link")
  )
  if (nrow(df) > 0) df$Institution <- row$Institution
  df
})
isolvedhire_df <- bind_rows(isolvedhire_results)

# University of Montana's NEOGOV Attract board also covers three branch/
# affiliate campuses under the same feed -- real street addresses
# confirmed live: Missoula College, Helena College, and University of
# Montana Western (Dillon), so none of the three get their own registry
# row, same "check the parent board before assuming a gap" logic as
# Highlands College under Montana Tech.
# Institution is NOT overwritten from the registry row here (unlike every
# other platform below) -- parse_neogov_postings() already attributes
# each posting to its real institution (University of Montana vs. Helena
# College/Missoula College/UM Western, 2026-08-07) via
# neogov_location_to_institution(), and blindly reassigning row$Institution
# here would silently erase that split.
neogov_institutions <- he_registry[he_registry$Platform == "Neogov", ]
neogov_results <- lapply(seq_len(nrow(neogov_institutions)), function(i) {
  row <- neogov_institutions[i, ]
  safe_scrape(
    row$Institution,
    scrape_fn = function() fetch_neogov_postings(row$Feed_URL, row$Institution),
    expected_cols = c("Title", "Location", "Posted_Date", "Link", "Institution")
  )
})
neogov_df <- bind_rows(neogov_results)

# Carroll College has no structured ATS -- CarrollCollegeHeuristic scrapes
# its accordion-widget positions page directly (misc_college_scrapers.R),
# same heuristic-source caveat as Miles/Dawson CC above.
carroll_institutions <- he_registry[he_registry$Platform == "CarrollCollegeHeuristic", ]
carroll_results <- lapply(seq_len(nrow(carroll_institutions)), function(i) {
  row <- carroll_institutions[i, ]
  df <- safe_scrape(
    row$Institution,
    scrape_fn = function() fetch_carroll_college_postings(row$Feed_URL),
    expected_cols = c("Title", "Location", "Posted_Date", "Link")
  )
  if (nrow(df) > 0) df$Institution <- row$Institution
  df
})
carroll_df <- bind_rows(carroll_results)

# Rocky Mountain College also has no structured ATS -- its own
# WordPress/Elementor employment page is heuristic-scraped the same way
# (misc_college_scrapers.R), though its markup is cleaner than the other
# heuristic sources (real per-posting detail URLs and department terms).
rockymtn_institutions <- he_registry[he_registry$Platform == "RockyMountainCollegeHeuristic", ]
rockymtn_results <- lapply(seq_len(nrow(rockymtn_institutions)), function(i) {
  row <- rockymtn_institutions[i, ]
  df <- safe_scrape(
    row$Institution,
    scrape_fn = function() fetch_rocky_mountain_college_postings(row$Feed_URL),
    expected_cols = c("Title", "Location", "Posted_Date", "Link")
  )
  if (nrow(df) > 0) df$Institution <- row$Institution
  df
})
rockymtn_df <- bind_rows(rockymtn_results)

# University of Providence runs ADP Workforce Now -- Feed_URL packs
# "cid:ccId" since the platform's job-requisitions API needs both to
# identify the employer's career-center site.
adp_institutions <- he_registry[he_registry$Platform == "AdpWorkforceNow", ]
adp_results <- lapply(seq_len(nrow(adp_institutions)), function(i) {
  row <- adp_institutions[i, ]
  feed_parts <- strsplit(row$Feed_URL, ":")[[1]]
  df <- safe_scrape(
    row$Institution,
    scrape_fn = function() fetch_adp_workforcenow_postings(feed_parts[1], feed_parts[2], row$Institution),
    expected_cols = c("Title", "Location", "Posted_Date", "Link")
  )
  if (nrow(df) > 0) df$Institution <- row$Institution
  df
})
adp_df <- bind_rows(adp_results)

# Salish Kootenai College, Little Big Horn College, and Fort Peck
# Community College also have no structured ATS -- each gets its own
# heuristic scraper in misc_college_scrapers.R tailored to its real page
# structure, same caveats as the other heuristic sources above.
skc_institutions <- he_registry[he_registry$Platform == "SKCHeuristic", ]
skc_results <- lapply(seq_len(nrow(skc_institutions)), function(i) {
  row <- skc_institutions[i, ]
  df <- safe_scrape(
    row$Institution,
    scrape_fn = function() fetch_skc_postings(row$Feed_URL),
    expected_cols = c("Title", "Location", "Posted_Date", "Link")
  )
  if (nrow(df) > 0) df$Institution <- row$Institution
  df
})
skc_df <- bind_rows(skc_results)

lbhc_institutions <- he_registry[he_registry$Platform == "LBHCHeuristic", ]
lbhc_results <- lapply(seq_len(nrow(lbhc_institutions)), function(i) {
  row <- lbhc_institutions[i, ]
  df <- safe_scrape(
    row$Institution,
    scrape_fn = function() fetch_lbhc_postings(row$Feed_URL),
    expected_cols = c("Title", "Location", "Posted_Date", "Link")
  )
  if (nrow(df) > 0) df$Institution <- row$Institution
  df
})
lbhc_df <- bind_rows(lbhc_results)

fpcc_institutions <- he_registry[he_registry$Platform == "FPCCHeuristic", ]
fpcc_results <- lapply(seq_len(nrow(fpcc_institutions)), function(i) {
  row <- fpcc_institutions[i, ]
  df <- safe_scrape(
    row$Institution,
    scrape_fn = function() fetch_fpcc_postings(row$Feed_URL),
    expected_cols = c("Title", "Location", "Posted_Date", "Link")
  )
  if (nrow(df) > 0) df$Institution <- row$Institution
  df
})
fpcc_df <- bind_rows(fpcc_results)

# Stone Child College runs Apptegy, the same browser-requiring CMS as
# misc_district_scrapers.R's Wolf Point/Plentywood -- own chromote session
# (not shared with the K-12 chunk's, which runs as a separate,
# independently re-runnable chunk).
stonechild_institutions <- he_registry[he_registry$Platform == "Apptegy", ]
stonechild_results <- lapply(seq_len(nrow(stonechild_institutions)), function(i) {
  row <- stonechild_institutions[i, ]
  df <- safe_scrape(
    row$Institution,
    scrape_fn = function() {
      session <- ChromoteSession$new()
      on.exit(tryCatch(session$close(), error = function(e) NULL), add = TRUE)
      fetch_stonechild_postings(session, row$Feed_URL)
    },
    expected_cols = c("Title", "Location", "Posted_Date", "Link")
  )
  if (nrow(df) > 0) df$Institution <- row$Institution
  df
})
stonechild_df <- bind_rows(stonechild_results)

# Aaniiih Nakoda College and Chief Dull Knife College also have no
# structured ATS -- each gets its own heuristic scraper in
# misc_college_scrapers.R tailored to its real page structure. CDKC's
# scraper is expected to return zero rows most weeks (see that scraper's
# own header comment) -- its one real current File block is a Trustee
# board-seat notice, not a job posting.
ancollege_institutions <- he_registry[he_registry$Platform == "AnCollegeHeuristic", ]
ancollege_results <- lapply(seq_len(nrow(ancollege_institutions)), function(i) {
  row <- ancollege_institutions[i, ]
  df <- safe_scrape(
    row$Institution,
    scrape_fn = function() fetch_ancollege_postings(row$Feed_URL),
    expected_cols = c("Title", "Location", "Posted_Date", "Link")
  )
  if (nrow(df) > 0) df$Institution <- row$Institution
  df
})
ancollege_df <- bind_rows(ancollege_results)

cdkc_institutions <- he_registry[he_registry$Platform == "CDKCHeuristic", ]
cdkc_results <- lapply(seq_len(nrow(cdkc_institutions)), function(i) {
  row <- cdkc_institutions[i, ]
  df <- safe_scrape(
    row$Institution,
    scrape_fn = function() fetch_cdkc_postings(row$Feed_URL),
    expected_cols = c("Title", "Location", "Posted_Date", "Link")
  )
  if (nrow(df) > 0) df$Institution <- row$Institution
  df
})
cdkc_df <- bind_rows(cdkc_results)

hedata_raw <- bind_rows(peopleadmin_df, jazzhr_df, paycom_df, milescc_df, dawsoncc_df,
                         isolvedhire_df, neogov_df, carroll_df, rockymtn_df, adp_df,
                         skc_df, lbhc_df, fpcc_df, stonechild_df, ancollege_df, cdkc_df)
```

### Combine all HE data, classify, archive, and accumulate history
```{r munge he data, message=FALSE, warning=FALSE, echo=TRUE}
library(dplyr)
library(writexl)

hedata <- hedata_raw %>%
  select(Title, Location, Posted_Date, Institution, Link) %>%
  mutate(Posted_Date = as.character(Posted_Date),
         Archive_Date = Sys.Date())

if (!dir.exists("Archived_HE_Data")) dir.create("Archived_HE_Data")
if (!dir.exists("Mt_Ed_Jobs")) dir.create("Mt_Ed_Jobs")

file_name <- paste0("hedata_", Sys.Date(), ".xlsx")
write_xlsx(hedata, path = file.path("Archived_HE_Data", file_name))
write_xlsx(hedata, path = file.path("Mt_Ed_Jobs", "hedata.xlsx"))

# Fix historical institution-name typos before anything downstream keys off
# Institution -- applied AFTER the xlsx archive writes above, so the
# archived raw snapshot keeps whatever spelling the scraper actually
# produced that week.
hedata <- hedata %>% mutate(Institution = canonicalize_he_institution(Institution))

this_week_he_cat <- hedata %>% mutate(Job_Type = classify_he_job_type(Title))
this_week_facultydata <- this_week_he_cat %>%
  filter(Job_Type %in% c("Instructor/Teacher/Faculty", "Adjunct/Part-Time Faculty")) %>%
  mutate(Category = classify_he_faculty_category(Title))

source("history_accumulator.R")

facultydata <- append_weekly_rows(file.path("Mt_Ed_Jobs", "facultydata.csv"), as.data.frame(this_week_facultydata))
write.csv(facultydata, file.path("Mt_Ed_Jobs", "facultydata.csv"), row.names = FALSE)

this_week_he_totals <- hedata %>%
  count(Institution, Archive_Date, name = "n")
he_institution_weekly_totals <- append_weekly_rows(
  file.path("Mt_Ed_Jobs", "he_institution_weekly_totals.csv"), this_week_he_totals)
write.csv(he_institution_weekly_totals, file.path("Mt_Ed_Jobs", "he_institution_weekly_totals.csv"), row.names = FALSE)

this_week_hesum <- this_week_facultydata %>%
  group_by(Category, Archive_Date, Job_Type) %>%
  summarize(sum = n(), .groups = "drop") %>%
  mutate(Institution = "Total") %>%
  select(Category, Archive_Date, Institution, Job_Type, sum)

this_week_hesuminst <- this_week_facultydata %>%
  group_by(Category, Archive_Date, Institution, Job_Type) %>%
  summarise(sum = n(), .groups = "drop")

check_total_matches_parts(this_week_hesum, this_week_hesuminst,
                           group_cols = c("Category", "Archive_Date", "Job_Type"))

this_week_allsum_he <- bind_rows(this_week_hesum, this_week_hesuminst)
Allsum_he <- append_weekly_rows(file.path("Mt_Ed_Jobs", "allsum_he.csv"), this_week_allsum_he)
write.csv(Allsum_he, file = file.path("Mt_Ed_Jobs", "allsum_he.csv"), row.names = FALSE)

henowsum <- this_week_hesum %>%
  ungroup() %>%
  rename(Sum = sum) %>%
  select(Category, Job_Type, Sum, Institution)

henowinstsum <- this_week_facultydata %>%
  group_by(Category, Institution, Job_Type) %>%
  summarize(Sum = n(), .groups = "drop") %>%
  select(Category, Sum, Institution, Job_Type)

Allnow_he <- bind_rows(henowsum, henowinstsum)
write.csv(Allnow_he, file = file.path("Mt_Ed_Jobs", "allnow_he.csv"), row.names = FALSE)
```

### HE faculty salary, enrollment, and Pell Grant recipient share (IPEDS via Urban Institute)
```{r he salary enrollment pell data, message=FALSE, warning=FALSE, echo=TRUE}
library(dplyr)
source("scrape_helpers.R")
source("ipeds_salary_scraper.R")
source("ipeds_enrollment_scraper.R")
source("fsa_pell_scraper.R")

he_salary <- safe_scrape(
  "IPEDS instructional staff salaries (MT)",
  scrape_fn = fetch_ipeds_he_salaries,
  expected_cols = c("Name", "Faculty_Avg_Salary", "Faculty_Avg_Salary_Professor",
                     "Faculty_Count", "Salary_Year")
)

he_enrollment <- safe_scrape(
  "IPEDS fall enrollment FTE (MT)",
  scrape_fn = fetch_ipeds_he_enrollment,
  expected_cols = c("Name", "Enrollment", "Enrollment_Year")
)

he_enrollment_trend <- safe_scrape(
  "IPEDS fall enrollment 5-year trend (MT)",
  scrape_fn = fetch_ipeds_he_enrollment_trend,
  expected_cols = c("Name", "Enrollment_Change_Pct")
)

he_pell_share <- safe_scrape(
  "FSA Pell Grant recipient share (MT)",
  scrape_fn = fetch_ipeds_he_pell_share,
  expected_cols = c("Name", "Pell_Recipient_Share", "Pell_Year")
)

# Static geo/link fields (Name/County/Latitude/Longitude/Link) come from
# he_institution_registry.csv, the same "read salarymap.csv back first if
# it exists, don't blank out a failed fetch's columns" pattern
# salarymap2.csv's chunk above uses.
he_registry <- read.csv("he_institution_registry.csv", stringsAsFactors = FALSE) %>%
  transmute(Name = Institution, County, Longitude, Latitude, Link = Job_Link)

salarymap_path <- file.path("Mt_Ed_Jobs", "salarymap.csv")
salarymap <- if (file.exists(salarymap_path)) {
  read.csv(salarymap_path, fileEncoding = "UTF-8") %>%
    select(-any_of(c("County", "Longitude", "Latitude", "Link"))) %>%
    right_join(he_registry, by = "Name") %>%
    select(Name, County, Longitude, Latitude, Link, everything())
} else {
  he_registry
}

if (nrow(he_salary) > 0) {
  salarymap <- salarymap %>%
    select(-any_of(c("Faculty_Avg_Salary", "Faculty_Avg_Salary_Professor",
                      "Faculty_Count", "Salary_Year", "Salary_Source"))) %>%
    left_join(he_salary, by = "Name") %>%
    mutate(Salary_Source = "IPEDS via Urban Institute Education Data Portal (educationdata.urban.org)")

  # Multi-year salary trend (current + 2 prior years) -- IPEDS is queryable
  # by year indefinitely, unlike the DLI Teacher Compensation Report (only
  # one edition published so far -- see salary_scrapers.R). Pivoted to
  # generic "N years ago" column names, not literal year numbers, so the
  # schema stays stable as the calendar year rolls over.
  salary_trend <- fetch_ipeds_he_salary_trend(n_years = 3)
  if (nrow(salary_trend) > 0) {
    latest_year <- max(salary_trend$Year)
    salary_trend_wide <- salary_trend %>%
      mutate(YearsAgo = latest_year - Year) %>%
      filter(YearsAgo > 0) %>%
      select(Name, YearsAgo, Faculty_Avg_Salary) %>%
      tidyr::pivot_wider(names_from = YearsAgo, values_from = Faculty_Avg_Salary,
                          names_glue = "Faculty_Avg_Salary_Y{YearsAgo}Ago")
    salarymap <- salarymap %>%
      select(-any_of(c("Faculty_Avg_Salary_Y1Ago", "Faculty_Avg_Salary_Y2Ago"))) %>%
      left_join(salary_trend_wide, by = "Name")
  }
} else {
  message("IPEDS salary fetch failed -- leaving salarymap.csv's salary columns untouched this run.")
}

if (nrow(he_enrollment) > 0) {
  salarymap <- salarymap %>%
    select(-any_of(c("Enrollment", "Enrollment_Year"))) %>%
    left_join(he_enrollment, by = "Name")
} else {
  message("IPEDS fall enrollment fetch failed -- leaving salarymap.csv's Enrollment untouched this run.")
}

if (nrow(he_enrollment_trend) > 0) {
  salarymap <- salarymap %>%
    select(-any_of("Enrollment_Change_Pct")) %>%
    left_join(he_enrollment_trend, by = "Name")
} else {
  message("IPEDS fall enrollment trend fetch failed -- leaving salarymap.csv's Enrollment_Change_Pct untouched this run.")
}

if (nrow(he_pell_share) > 0) {
  salarymap <- salarymap %>%
    select(-any_of(c("Pell_Recipient_Share", "Pell_Year"))) %>%
    left_join(he_pell_share, by = "Name")
} else {
  message("FSA Pell Grant recipient share fetch failed -- leaving salarymap.csv's Pell columns untouched this run.")
}

write.csv(salarymap, salarymap_path, row.names = FALSE)
```

### HE institution county-level context (income, rent, mining/energy employment share, population trend), from the Census Bureau
```{r he census county context, message=FALSE, warning=FALSE, echo=TRUE}
library(dplyr)
source("scrape_helpers.R")
source("census_acs_scraper.R")

# Reuses the exact same fetch_census_county_context() pipeline as the K-12
# chunk earlier in this file -- fetched independently rather than reusing
# that chunk's `county_context` variable, matching every other chunk in
# this file being self-contained and re-runnable on its own.
county_context_he <- safe_scrape(
  "Census ACS county context for HE institutions (MT)",
  scrape_fn = fetch_census_county_context,
  expected_cols = c("County", "Median_Household_Income", "Median_Gross_Rent",
                     "Population", "ACS_Year", "Mining_Employment_Share", "Population_Change_Pct")
)

if (nrow(county_context_he) > 0) {
  salarymap <- read.csv(salarymap_path, fileEncoding = "UTF-8") %>%
    select(-any_of(c("Median_Household_Income", "Median_Gross_Rent", "Population",
                      "ACS_Year", "Mining_Employment_Share", "Population_Change_Pct"))) %>%
    left_join(county_context_he, by = "County")
  write.csv(salarymap, salarymap_path, row.names = FALSE)
} else {
  message("Census ACS county context fetch failed -- leaving salarymap.csv untouched this run.")
}
```
